\documentclass[12pt]{article}


\include{../style}


\begin{document}


\input{title}

\begin{problem}{1}
Please tell me a bit about your analysis background. For example, which Dartmouth courses have you taken? What courses have you taken elsewhere and what did they cover? In particular, what multivariable calculus have you had? Have you ever taken an (undergraduate) complex variables course such as our Math 43?
\end{problem}
\begin{solution}
    My analysis background is weaker than my topology or algebra background. I did an undergraduate real analysis course on my own, using lecture recordings available online  3 years ago (freshman summer). Then I did your Functional Analysis course last year, which involved a lot of steep catch-up but ended up being fine a few weeks in. 
\end{solution}

\begin{problem}{2}
What are you hoping to get out of this course? ``I’m only here because I have to take a classroom course and this was the best option'' is an acceptable but disappointing answer. Of course, I am hoping for more.
\end{problem}
\begin{solution}
    I want to learn complex analysis because it is crucial to so many fields of Math. In particular, I want to understand the theory of complex manifolds / Hodge Theory with more analytic rigor.
\end{solution}


\begin{problem}{3}
What is your attitude towards analysis? Again, ``I hope to never had to take or teach an analysis course again'' is acceptable. But so is, ``I hope to work in analysis someday''.
\end{problem}
\begin{solution}
    I'm fairly new to it still. I enjoy the style of argument and find it quite different to algebra, which I have more experience with. I like that we study objects and state theorems that are easy to define, even if hard to prove or work with. In algebra, I typically find the objects are hard to construct but are designed to be easy to work with. 
\end{solution}


\begin{problem}{4}
If you are willing, tell me something interesting about yourself. For example, I came to Dartmouth in the fall of 1985. For a time, I was interested in underwater photography, but I can’t dive anymore so I’ve moved on to photos above water.
\end{problem}
\begin{solution}
    I'm from Karachi, Pakistan. I'm interested in logic puzzles, hiking, and computer science. I'm headed to graduate school at Rice for the next few years. 
\end{solution}




\end{document}