\documentclass[12pt]{amsart}


\include{../style}

\begin{document}

\input{title}


\section{Intro to Toric Geometry:}

There are $2$ mottos in toric geometry. 
\begin{enumerate}
    \item Toric geometry is the study of solutions to polynomoial equations in the presence of a large torus.
    \item The action of a torus should give combinatorial/algebraic structure.
\end{enumerate}

To make sense of this, we need to understand what solutions to polynomial equations are and what is a large torus. 

A geometric torus is $\underbrace{S^1 \times S^1 \times \cdots \times S^1}_{n \text{ times}}$. An algebraic torus is $(\C^\times)^\times$ or, more generally, $(k^\times)^n$ for some field $k$. 

We will now do an interlude in basic algebraic geometry. 

Let $k$ be a field. We call $\A_k^n = k^n$ the affine $n$-space. Next, we define algebraic sets and the Zariski topology. 

We give some examples of algebraic sets: The vanishings of $x^2+y^2$, $xy$, $x^2y-y$, and $z^2-x^2-y^2$ in the appropriate affine spaces. 

\begin{definition}
    An affine algebraic vareirt is an algebraic subset of $\A^n_k$ such that it is irreducible in the Zariski topology.
\end{definition}

\begin{theorem}[Nullstellensatz]
    There is an order reversing bijection:
    \[ \left\{\text{Algebraic varieties in $\A^n_k$} \right\} \leftrightarrow \left\{ I \subseteq k[x_1, \cdots, x_n] \text{ such that $I$ is prime. }\right\}\]
\end{theorem}

Coming back to toruses, note that $k^\times \subset \A^1$ is a torus living in our affine space. Thus, $A^1$ is a toric variety. Similarly, $(k^\times)^n = \A^n \setminus \V(x_1\cdots x_n) \subseteq \A^n$ is an big torus. Hence, $\A^n$ is a toric variety. 

\begin{definition}
    If $X \subseteq \A^n$ is an algebraic set, the coordinate ring is: 
    \[ k[X] = k[x_1,\cdots, x_n]/I_X\]
    where $I_X = \langle f \in k[x_1, \cdots, x_n] | f(p) = 0 \, \forall x \in X \rangle$.
\end{definition}

\begin{lemma}
    If $f \in S = k[x_1, \cdots, x_n]$, then the set $D(f) = \A^n \setminus \V(f)$ is such that $k[D(f)] \equiv S\left[\frac{1}{f}\right]$
\end{lemma}

Then, as examples, we get that the large tori:
\begin{enumerate}
    \item $k[(k^\times)] = k[x, x^{-1}]$
    \item $k[(k^\times)^n] = k[x_1, x_1^{-1}, \cdots, x_n, x_n^{-1}]$
\end{enumerate}

Now we can define what a toric variety is. 
\begin{definition}
    An affine toric vareity is an affine algebraic variety $X$ together with an open dense torus $T \subseteq X$ such that the action of $T$ on itself extends to $X$. That is, there is an action $k^\times \times \A^1 \to \A$ that restricts to the torus' action on itself on $k^\times \times k^\times$. 
\end{definition}

We now discuss what the action of the torus means. Let $T = (k^\times)$. Then $T$ is also a group with multiplication $(s,t) \mapsto st$ and inverse $t \mapsto t^{-1}$.

\begin{example}
    Let $k^\times \subset \A^1$. Then, $k^\times$ acts on itself. We extend this by letting the action on $0$ be such that $t \times 0 = 0$ for all $t \in k^\times$. 
\end{example}

Now we make all of this precise. We have the following definition:
\begin{definition}
    An algebraic group is an algebraic variety $G$ together with maps: 
    \[ \times: G \times G \to G \qquad (-)^{-1}: G \to G\]
    that are regular and satisfy the usual group axioms.
\end{definition}

\begin{example}
    $G = (k^\times)^n$ with coordinate with multiplication and inverses. 
\end{example}

\begin{definition}
    A split torus over a field $k$ is algebraic group $G$ isomorphisc over $k$ to $(k^\times)^n$ for some $n$. 
\end{definition}

\begin{definition}
    An algebraic torus over a field $k$ is an algebraic group $T$ such that after an extension, $T \times_k F \cong (F^\times)^n$. 
\end{definition}

\begin{remark}
    To motivate this definition, consider $S^1$. We want $S^1$ to be a torus. That is, $S^1 = \V(x^2+y^2-1) \subseteq \A^2_\R$ is not $(\R^\times)^n$ for any $n$. However, if we consider $S^1 = \V(x^2+y^2-1) \subseteq \A^2_\C$, we can factor the polynomial to write it as $\V(zw-1)$. Considering $\C[z,w]/\langle zw-1\rangle \cong \C[x, x^{-1}]$. 
\end{remark}

\begin{definition}
    An affine toric variety is an affine algebraic variety $X$ together with a torus $T \subseteq X$ that is open and dense together with an algebraic action: 
    \[ \xymatrix{ T \times X \ar[r] & T \\ T \times T \ar[u] \ar[r] & T \ar[u] } \]
\end{definition}

\begin{definition}
    Let $X \subseteq \A^n$ and $Y \subseteq \A^m$ be affine algebraic varieties. A morphism is globally given by polynomials $(f_1, \cdots, f_m)$ that restrict to a map from $X$ to $Y$.
\end{definition}

\begin{lemma}
    $\Phi: X \to Y$ is a morphism of algebraic varities if and only if there is an induced (pullback) map of rings: 
    \[ \Phi^*: k[Y] \to k[X]\]
\end{lemma}

\begin{example}[Toric Varieties]
    .
    \begin{enumerate}
        \item $X = (k^\times)^n$
        \item $X = \A^1$
        \item $X = \A^n$. Extend entry-wise. 
        \item $X = \V(x^3-y^2)$
    \end{enumerate}
\end{example}


\section{Intro to Algebraic Geometry:}
We are taking a detour and doing classical AG fast but properly before going into Toric Geometry. 

Let $k$ be a field. You can imagine $k = \C$ for most of this. 
\begin{definition}
    An algebraic set is a subset: 
    \[ \V(f_1, \cdots, f_t) = \{ x \in \A^n_k | f_1(x) = f_2(x) = \cdots = f_t(x) = 0 \}\]
    where $f_i \in k[x_1, \cdots, x_n]$. 
\end{definition}

Given an ideal $I \subseteq k[x_1, \cdots, x_n]$. We define, 
\[ \V(I) = \{ x \in \A^n_k | f(x) = 0 \, \forall f \in I\}\]
\begin{remark}
    By the Hilbert Basis theorem,
    \[ I = \langle f_1, \cdots, f_t\rangle\]
    because the ring is noetherian. Thus, $\V(I) = \V(f_1, \cdots, f_t)$ is an algebraic set. 
\end{remark}

\begin{definition}
    If $V \subseteq \A^n$ is an algebraic set. We define, 
    \[ \I(V) = \{ f \in k[x_1, \cdots, x_n] \, | f(x) = 0 \, \forall x \in V\} \]
\end{definition}

\begin{lemma}
    $\I(V)$ is an ideal
\end{lemma}

\begin{lemma}
    If $V \subseteq \A^n_k$, then 
    \[ \V(\I(V)) = V\] 
\end{lemma}
\begin{proof}
    \todo{Do this.}
\end{proof}

Warning: 
\[ \I(\V(I)) \neq I\]

\begin{example}
    \begin{enumerate}
        \item $k = \R$. Let $I = \langle x^2 + 1\rangle$. Then $\V(I) = \emptyset$ and $\I(\emptyset) = \R[x]$. 
        \item $k = \overline{k}$ and $I = \langle x^2 \rangle \subseteq \A^1$. $\V(I) = \{0\}$ and $\I(\{0\}) = \langle x \rangle$. 
    \end{enumerate}    
\end{example}

\begin{proposition}
    If $k = \overline k$ and $I \subseteq k[x_1, \cdots, x_n]$ is an ideal 
    \[ \I(\V(I)) = \{f \in k[x_1, \cdots, x_n] | \exists m : f^m \in I \} = \sqrt{I}\]
\end{proposition}

\begin{theorem}[Hilbert's Nullstellensatz]
    Assume $k = \overline{k}$. Then, 
    \begin{enumerate}
        \item Let $m \subseteq k[x_1, \cdots, x_n]$ be an ideal. $m$ is maximal if and only if $m = \langle x_1-a_1, \cdots, x_n-a_n\rangle$ for some $(a_1, \cdots, a_n) \in \A^n_k$. 
        \item There is an inclusion reversing bijection between algebraic subsets of $\A^n_k$ and radical ideals in $k[x_1, \cdots, x_n]$ given by $\I$ and $\V$. 
    \end{enumerate}
\end{theorem}

\begin{definition}
    A polynomial function on $\A^n_k$ is a function of the form $f: \A^n_k \to k$ given by $\overline{x} \mapsto f(\overline{x})$ where $f \in k[x_1, \cdots, x_n]$. 
\end{definition}

Now we wanna define polynomial functions on algebraic sets. We do this as follows:
\begin{definition}
    Let $V \subseteq \A^n$ is an algebraic set. A function $f: V \to k$ is a polynomial function if and only if there exists a polynomial function $F: \A^n \to k$ such that the following commutes, 
        \[ \xymatrix{ \A^n \ar[rd]^F \\ V \ar[u] \ar[r]^f & k }\]
\end{definition}

The choice of lift is not unique. 
\begin{example}
    Let $V = \V(y-x^2)$. Let $F(x,y) = y$ and $G(x,y) = 2y-x^2$. Restricted to $V$ they are the same function as $2y-x^2 = y+(y-x^2) = y$. 
\end{example}

\begin{example}
    Consider $F(x,y) = e^{x^2+y^2}$ and $V = \V(x^2+y^2-1)$. Then $F|_V(x,y) = e$, which is a polynomial. 
\end{example}

\begin{example}
    Consider $V = \V(xy-1) \subseteq \A^2$. Consider $F(x,y) = \frac{1}{x}$. This is not a function on $\A^2$ but it is a function on $V$. Moreover, it is a polynomial function because $\frac{1}{x} = y$ on $V$. 
\end{example}

\begin{definition}
    The coordinate ring of an algebraic set $V \subseteq \A^n$, $k[V]$ is the set of polynomials functions on $V$ with pointwise multiplication and addition. 
\end{definition}

\begin{lemma}
    If $V \subset \A^n$ is an algebraic set, then the coordinate ring $k[V]$ is isomorphic to $k[x_1, \cdots, x_n]/\I(V)$. 
\end{lemma}
\begin{proof}
    We have a map,
    \[ k[x_1, \cdots, x_n] \twoheadrightarrow k[V] \]
    sending $f \mapsto [x \mapsto f(x)]$. This fits in the exact sequence,
    \[ 0 \to \I(V) \to k[x_1, \cdots, x_n] \to k[V] \to 0\]
\end{proof}

\begin{lemma}
    If $k \supseteq \R$, then an algebraic set is closed in the Euclidean topology $\A^n_k$. 
\end{lemma}
\begin{proof}
    The finite intersection of closed sets is closed.
\end{proof}

\begin{definition}
    The Zariski topology $\A^n_k$ has closed sets equal to all the algebraic sets. 
\end{definition}

Furthermore, we set the Zariski topology on an algebraic set $V \subseteq \A^n$ to be the subspace topology $V \cap Z$ where $Z \subseteq \A^n_k$ is an algebraic set. 

Given a set $S \subseteq \A^n_k$, we have $\overline{S} = \V(\I(S))$. 

\begin{definition}
    A morphism of algebraic sets $V \subset \A^n, W \subset \A^m$ is a function $f: V \to W$ such that, 
    \[ \xymatrix{ \A^n \ar[r]^F & \A^m \\ V \ar[u] \ar[r]^f & W \ar[u] }\]
    where $F: (x_1, \cdots, x_n) \mapsto (F_1(\overline x), \cdots, F_m(\overline x))$ with $F_1, \cdots, F_m \in k[x_1, \cdots, x_m]$.
\end{definition}

\begin{definition}
    Algebraic sets are isomorphisc if and only if there exists morphisms that are mutually inverses. 
\end{definition}

\begin{remark}
    These functions are continuous in the Zariski topology because closed sets are given by the vanishing of polynomials and pulling back polynomials by polynomials still give polynomials. 
\end{remark}

\begin{remark}
    These maps are not closed. Consider $F(x,y) \mapsto y$. Then $\V(xy-1) \subseteq \A^2$ maps to $\A^1 \setminus \{0\} \subset \A^1$ not closed.  
\end{remark}

\begin{definition}
    A finitely generated reduced $k$-algebrai is $k[x_1, \cdots, x_n]/I$ where $I$ is radical.     
\end{definition}

\begin{theorem}[Nullstellensatz II]
    Assume $k = \overline{k}$. 
    \begin{enumerate}
        \item If $f: V \to W$ is a morphism of algebraic sets then there is a morphism of $k$-algebras, 
        \begin{align*}
            F^\#: k[V] &\to k[W] \\
            [g: W \to k] &\mapsto [g\circ f: V \to k]
        \end{align*}
        \item If $I = \I(V)$ and $J = \I(W)$ and there exists a map $\sigma: k[x_1, \cdots, x_m]/J \to k[x_1, \cdots, x_n]/I$ then, pick $F_i \in k[x_1, \cdots, x_n]$ such that $\sigma(y_i) = F_i \text{ mod } I$. Then the map, 
        \begin{align*}
            \overline{F}: \A^n &\to \A^m \\
            x &\mapsto (F_1(x), \cdots, F_m(x))
        \end{align*}
        restricts to a map $V \to W$ and this restriction is independent of choice. 
        \item Moreover, $F^\# = \sigma$. 
        \item $V \cong W \iff k[V] \cong k[W]$. 
        \item There is an (anti)-equivalence of categories between categories of algebraic sets and their morphisms and finitely generated reduced $k$-algebras. 
    \end{enumerate}
\end{theorem}

We have now defined the major correspondence that's studied in a first semester graduate course in classical AG. The work we have still left is translating from one language to another, i.e. dimension, singularities, etc. 


We have a glaring problem because we are working in an ambient affine space. So, we expand first to projective space. 

\begin{definition}
    Projective $n$-space/$k$ is 
    \[ \P^n_k = \{ \text{ one-dim subspaces of $k^{n+1}$ }\}\]
\end{definition}

\begin{lemma}
    \[ \P^n = (k^{n+1}\setminus \{0\})/~\]
    where $(a_0, \cdots, a_n) \sim (b_0, \cdots, b_n)$ if and only if there exists $\lambda \in k^\times$ such that one is a scalar multiple of the other. 
\end{lemma}

Next, we define the homogeneous coordinates. 
\begin{definition}
    The coordinates on $\P^n$ can be given as $[a_0 : a_1 : \cdots : a_n]$. This is only unique up to scaling by $k^\times$. In other words, $(a_0, \cdots, a_n)$ and $(b_0, \cdots, b_n) \in \A^{n+1}$ define the same point if the $2x2$ minors of 
    \[ \begin{pmatrix} 
        a_0 & \cdots & a_n \\ 
        b_0 & \cdots & b_n 
    \end{pmatrix} \] 
    are all $0$. 
\end{definition}

\begin{example}
    Consider $\P^1_\R$. We drew the picture where we picked the reference line $x_0 = 1$ and mapped all lines to the point on this line, i.e. a line goes to $(1, \lambda)$ where $\lambda$ is its slope. We got a map, 
    \begin{align*}
        \P^1_R &\to \R \cup \{\infty\} 
        [x_0 : x_1] \mapsto \begin{cases}
            \frac{x_1}{x_2} \qquad x_0 \neq 0 \\
            \infty \qquad x_0 = 0
        \end{cases}
    \end{align*}
    Thus, we got $\P^1$ as a circle. Then, we did the same thing for $\P^2$ showing $\P^2 \cong \R^2 \cup \P^1$. 
\end{example}

\begin{lemma}
    For $i = 0, \cdots, n$, 
    \[ U_i = \{ [x_0 : \cdots : x_n ] \subseteq \P^n_k | x_i = 0\}\]
    \begin{enumerate}
        \item $\psi_i : \P^n_k \to \A^n \cup \P^{n-1}$ is a bijection (details)
        \item $\psi_i|_{U_i}$ is a bijection.  
        \item $\P^n = \bigcup_i U_i$
        \item $\psi_j \circ \psi_i^{-1}: \psi_i(U_i \cap U_j) \to \psi_j(U_i \cap U_j)$ is a rational function in the coordinates on $\A^n$. 
    \end{enumerate}
\end{lemma}

\begin{example}
    Explicltly showed that the functions compose to a rational function. 
\end{example}

\begin{theorem}[Fact.]
    If $k = \R, \C$ then $\P^n_\R$ or $\P^n_\C$ are compact $\R$ or $\C$ manifolds. 
\end{theorem}

We cannot define the algebraic sets for $\P^n$ using global functions. For instance, $\P^n_\C \to \C$ every holomorphic function is constant. 

\begin{definition}
    A polynomial $f \in k[x_0, \cdots, x_n]$ is homogenenous $\iff$ every term of $f$ has the same degree $\iff$ $f(\lambda x) = \lambda^{\deg(f)}f(x)$ for $\lambda \in k^\times$. 
\end{definition}

Now, we are defining functions. 
\begin{example}
    $\P^1_\C \to \C$ given by $[x: y] \mapsto x$ is homogenous but is not well-defined. 
\end{example}

\begin{definition}
    A projective algberaic set is a subset $V \subset \P^n_k$ of the form, 
    \[ V = \V(f_1, \cdots, f_t) = \{ x \in \P^n : f_1(x) = \cdots = f_t(x) = 0 \}\]
    for $f_i \in k[x_0, \cdots, x_n]$ homogeneous.  
    If $I \subset k[x_0, \cdots, x_n]$ is a homogeneous ideal then
    \[ \V(I) = \{ x \in \P^n : f(x) = 0 \, \forall f \in I\}\]
\end{definition}

\begin{definition}
    If $V \subseteq \P^n$ is a projective algebraic set, 
    \[ \I(V) = \langle f \in k[x_1, \cdots, x_n] | \, f \text{ hom. and } f(x) = 0 \, \forall x \in V\rangle \]
\end{definition}

\begin{theorem}[Proj. Nullstellensatz]
    Assume $k = \overline{k}$. 
    \begin{enumerate}
        \item If $I \subseteq k[x_0, \cdots, x_n]$ is a homogeneous ideal,
        \[ \V(I) = \emptyset \iff \langle x_0, \cdots, x_n \rangle^m \subseteq I)\]
        for some $m$.  
        \item $\I(\V(I)) = \sqrt{I}$. 
        \item There is a bijection between projective algebraic subsets in $\P^n$ and homogeneous radical ideals $k[x_0, \cdots, x_n]$ not equal to $\langle x_0, \cdots, x_n \rangle$. 
    \end{enumerate}
\end{theorem}

Beginning day 3 (Apr 3). 

\begin{definition}
    The homogenous coordinate ring of a projective algebraic set $V \subseteq \P^n_k$ is 
    \[ k[V] = k[x_0, \cdots, x_n]/\I(V)\]
\end{definition}
Warning: These are not functions on $V$. 

We define the Zariski topology the same way. 
\begin{definition}
    The Zariski topology on $\P^n_k$ has projective algebraic sets as its closed sets. The topology on an proj. alg. set is the subspace topology. 
\end{definition}

\begin{definition}
    A morphism $F: V \to W$ of projective algebraic sets $V \subseteq \P^n_k$ is a function such that $\forall p \in V$ there exists an open set $p \in U \subseteq V$ and polynomials $F_1, \cdots, F_m \in \C[x_0, \cdots, x_n]$ homogeneous of degree $d$ such that: 
    \[ F|_U: U \to \P^m\]
    An isomorphism is a function with an inverse function. 
\end{definition}

\begin{example}
    Let $C = \V(zx-y^2)$ There is map $F: C \to \P^1$ defined by,
    \[ [x:y:z ] \mapsto \begin{cases}
        [x:y] \qquad x \neq 0 \\
        [y:z] \qquad z \neq 0
    \end{cases}\]
    If $x \neq 0$ and $z \neq 0$, then $y \neq 0$. Then, 
    \begin{align*}
        [x: y] = [xy: y^2] = [xy : xz] = [y : z]
    \end{align*}
    Next, take the map, 
    \[ \P^1 \to \C \qquad [s:t] \mapsto [s^2 : st : t^2]\]
    This is well-defined. It is a morphism (given as polynomial globally). We can check these are inverses. 
    \begin{align*}
        [s: t] \mapsto [s^2 : st : t^2] \mapsto \begin{cases}
            [s^2 : st] = [s:t] \qquad s \neq 0 \\
            [st : t^2] = [s:t] \qquad t \neq 0
        \end{cases}
    \end{align*}
    Thus, these are isomorphisms. 

    However, note that: 
    \[ k[\P^1] = k[s, t] \not \cong k[C] = k[x,y,z]/\langle xz -y^2\rangle\]
    The projective coordinate ring depends on the embedding!
\end{example}


Recall, a locally closed set in a topological space $X$ is a closed subset of an open set. That is, it is given as $U \cap Z$ for $U$ open and $Z$ closed. 

\begin{definition}
    A quasiprojective variety is a locally closed subset of $\P^n_k$. 
\end{definition}

\begin{example}
    The following are quasiprojective varieties.
    \begin{enumerate}
        \item Open subsets of $\P^n_k$. 
        \item Projective algberaic sets. 
        \item Algebraic sets. (Some things need to be shown, we show them next.)
    \end{enumerate}
\end{example}

Take $V \subseteq \A^n_k$ and $V = \V(f_1, \cdots, f_t)$. Define, 
\[ f_i^h = x_0^{\deg(f_i)} f_i\left(\frac{x_1}{x_0}, \cdots, \frac{x_n}{x_0}\right)\]
Then $f^h(x_0, \cdots, x_n) = 0 \iff f_i(x_1, \cdots, x_n) = 0$.


\begin{example}
    $(k^\times)^n$ is quasiprojective. It is $\A^n \setminus \V(x_1, \cdots, x_n)$. 
\end{example}

\begin{definition}
    A function $\Phi: V \subset \P^n \to W \subset \P^m$ is a morphism of quasiprojective varieties if and only if $\forall p \in V$ there exists $F_1, \cdots, F_m$ homg. of degree $d$ in $k[x_0, \cdots, x_n]$ such that,
    \[ \Phi|_U: x \mapsto [F_0(x), \cdots, F_m(x)]\] 
\end{definition}

\begin{example}
    Take the sets $V = \V(xy-1)$ (closed in affine space) and $W = \A^1 \setminus \{0\}$ (open in affine space). First, we can homogenize to consider these in projective space. That is these live in $\P^2$ and $\P^1$ and are quasiprojective varieties. 
    \begin{align*}
        \xymatrix{ 
            \P^2 & \P^1 \ar[l] \\
            \{z \neq 0 \} \cap \V(xy-z^2) \ar[u] & \A^1 \setminus \{0 \} \ar[l] \ar[u] \\
        }
    \end{align*}
    \todo{Complete this.}

\end{example}

\begin{definition}
    A quasiprojective variety $V \subseteq \P^m_k$ is affine if and only if there's some algebraic set $W \subseteq \A^n_k$ such that $V \cong W$ as quasiprojective varieties. 
\end{definition}

If $V$ is a quasiprojective variety that is affine 
\[ k[V] := k[W]\]
for $W$. 

If $V \subseteq \A_k^n$ and $W \subseteq \A^n_k$. We need to show, 
\[ V \cong_{qp} W \iff V \cong_{AS} W \]

\begin{lemma}
    Let $V =\V(f_1, \cdots, f_t) \subseteq \A^n$ be an algebraic set and $g \in k[V]$ be some function. Let $V \setminus \V(g) =: U_f$ is affine. Moreover, 
    \[ k[U_f] \equiv k[V][g^{-1}]\]
\end{lemma}
\begin{proof}
    \begin{align*}
        \A^n &\to \A^{n+1} \\
        (x_1, \cdots, x_n) \in U_f  &\mapsto \left(x_1, \cdots, x_n, \frac{1}{g(x_1, \cdots, x_n)}\right)
    \end{align*}
    Make sure this lands in the right place. 
\end{proof}

\begin{definition}
    A quasiprojective variety $V \subseteq \P^m_k$ is projective if and only if there's some projective algebraic set $W \subseteq \P^n_k$ such that $V \cong W$ as quasiprojective varieties. 
\end{definition}


\begin{proposition}
    Every quasiprojective variety is covered by affine varieties. 
\end{proposition}

(April 7th)

\begin{definition}
    Let $U \subseteq V$ be open inside an affine variety and $U \to k$ some function. Then, 
    \begin{enumerate}
        \item For $p \in U$, $f$ is regular at $p$ if and only if $\exists p \in U' \subset U$ open and $g, h \in k[V]$ such that $f|_{U'} = \frac{g}{h}|_{U'}$ with $h \neq 0$ on $U'$.
        \item $f$ is regular on $U$ if and only if it is regular at $p \, \forall p \in U$. 
        \item Let $\OO_V(U)$ be the ring of regular functions on $U$ with pointwise operations. 
    \end{enumerate}
\end{definition}

\begin{theorem}
    \[ \OO_V(V) \cong k[V] \]
\end{theorem}

\begin{example}
    $f: U = \A^2 \setminus \V(x) \to k$ given by $(x,y) \to \frac{y}{x}$ is a regular function. 
\end{example}

\begin{definition}
    If $U \subseteq V$ is a quasiprojective variety with a function $f: U \to k$ then $f$ is regular at a point $p \in U$ if $p \in V' \subseteq V$ such that $f|_{V'}$ is regular on $V'$ and $V'$ affine. 
\end{definition}

\begin{definition}
    We define $\OO_V(U)$ to be the ring of regular function on $U$. 
\end{definition}

\begin{lemma}
    $\OO_V(U)$ is a sheaf. 
\end{lemma}

\begin{definition}
    A function $\psi: V \to W$ of quasiprojective varieties is a morphism of quasiprojective varieties if and only if $\forall p \in V$ if there exist affine opens 
    \[ \xymatrix{ V \ar[r]^\psi & W \\ U \ar[u]^\iota \ar[r] & U' \ar[u]^\iota }\]
    where the bottom arrow is given by regular functions. 
\end{definition}

\begin{definition}
    An abstract algebraic variety is a topological space $X$ with a sheaf of rings $\OO_X$ such that there is an open conver $X = \bigcup U_i$ such that $(U_i, \OO_X(U_i))$ are isomorphic (as ringed spaces) to $(W_i, \OO_{W_i}(W_i))$ for $W_i$ an affine variety. 
\end{definition}

\begin{remark}
    Informally, this is the data of
    \[ \{V_\alpha\}_{\alpha \in \Lambda}, \{V_{\alpha, \beta}\}_{\alpha, \beta \in \Lambda}, \{g_{\alpha\beta}\}\]
    with $V_\alpha$ affine varieties, $V_{\alpha\beta} \subset V_\alpha$ being open affine subsets and $g_{\alpha\beta}: V_{\alpha\beta} \to^\sim V_{\beta\alpha}$ such that: 
    \begin{enumerate}
        \item $g_{\alpha\alpha} = \Id_{V_{\alpha\alpha}}$
        \item cocycle condition 
    \end{enumerate}
    Then, $X = \bigcup_{\alpha} X_\alpha / \sim$ with $x \in X_\alpha \sim u \in X_\beta$ iff $g_{\alpha\beta}(x) = y$. 
\end{remark}

\section{Toric Varieties:}

\begin{definition}
    A toric variety is a variety $X$ together with a dense torus $T \subseteq X$ and an algebraic action satisfying: 
    \[ \xymatrix{ T \times X  \ar[r] & X \\ T\times T \ar@{^{(}->}[u] \ar[r] & T \ar@{^{(}->}[u] }\]    
\end{definition}

From now on, we assume $k = \overline{k}$. 

\begin{definition}
    A group variety is a variety $G$ together with morphisms, 
    \begin{align*}
        m: G \times G &\to G \\
        i: G &\to G \\
        e: * &\to G 
    \end{align*}
    i.e. multiplication, inverse, and identity satisfiying the group axioms. \\
    Thus, $G$ is a group. 
\end{definition}

\begin{example}
    $k^\times = \A^1 \setminus \{0\}$ is a group variety. Our maps are, 
    \begin{align*}
        m: (x,y) \mapsto xy \\
        i: x \mapsto \frac{1}{x} \\
        e: * \mapsto 1
    \end{align*}
\end{example}

\begin{proposition}
    Let $G$ be an affine variety. Then $G$ is a group variety if and only if $k[G]$ is a finitely generate commutative $k$-Hopf algebra. That is, it is a finitely generated polynomial ring mod an ideal satisfying the Hopf condition, i.e. there exist maps 
    \begin{align*}
        m^\#: k[G] &\to k[G\times G] \cong k[G] \otimes k[G] \\
        i^\#: k[G] &\to k[G] \\
        e^\#: k[G] &\to k
    \end{align*}
    satisfying the equivalent group conditions. 
\end{proposition}

Another way to write this is, 
\begin{definition}
    $R$ is Hopf algebra if 
    \begin{align*}
        \Delta: R \to R \otimes R \\
        S: R \to R \\
        \varepsilon: R \to R
    \end{align*}
    called the co-multiplication, antipode, and counit satisfying the group axioms. 
\end{definition}

In particular, $\Delta$ has a nice description,
\begin{align*}
    \Delta: k[G] &\to k[G \times G] \cong k[G] \otimes k[G] \\
    f &\mapsto \Delta(f) = m^\#(f)
\end{align*}
is given by 
\[ \xymatrix{ G \times G \ar[d] \ar[r]^{m^\#(f)}& k \\ G \ar[ur]^f }\]
In particular, 
\[ m^\#(f): G \times G \to k \qquad m^\#(f)(g,h) = f(gh)\]

\begin{definition}
    An algebraic torus is a variety $T$ isomorphic to $\G_m^n$ for some $n$ where $\G_m \cong k^\times$. 
\end{definition}

\begin{remark}
    \begin{enumerate}
        \item This is not true if $k \neq \overline{k}$. 
        \item If $T \cong \G_m^n \cong \A^n \setminus \V(x_1, \cdots, x_n)$.
        \item $k[T] \cong k[\G_m^n] \cong k[\A^n\setminus \V(x_1, \cdots, x_n)]$
    \end{enumerate}
    Moreover, recall, 
    \begin{align*}
        k[\A^n \setminus \V(x_1, \ldots, x_n)] &\cong k[x_1, \ldots, x_n]\left[\frac{1}{x_1\cdots x_n}\right] \\
        &\cong k\left[x_1, \ldots, x_n, \frac{1}{x_1}, \cdots, \frac{1}{x_n}\right] \\
        &\cong k[x_1^\pm, \ldots, x_n^\pm]
    \end{align*}
    where this is called the ring of Laurent polynomials.
\end{remark}


\begin{lemma}
    \[(k[\G_m^n])^\times = \{ cx_1^{m_1} \cdots x_n^{m_n} : c \in k^\times, m_i \in \Z\}\]
\end{lemma}

\begin{definition}
    A character of a group variety $G$ is a group variety map $\chi: G \to \G_m = k^\times$. Note that as $k^\times \cong \GL_1(k)$, this is a one dimensional representaion. 
\end{definition}

\begin{lemma}
    Every character $\chi: \G_m^n \to \G_m^n$ is of the form 
    \[ \chi(t_1, \cdots, t_n) \to t_1^{m_1}\cdots t_n^{m_n} \]
    for some $(m_1, \cdots, m_n) \in \Z^n$ and all such maps appear, 
    \[ \Hom_{Grp. Var}(\G_m^n, \G_m) \equiv \Z^n \] 
\end{lemma}

\begin{proof}
    Let $\chi: \G_m^n \to \G_m$ be a character. This gives, 
    \[ \chi^\#: k[\G_m] \to k[G_m^n]\] 
    But this is, 
    \[ \chi^\#: k[t, t^{-1}] \to k[x_1^\pm, \ldots, x_n^\pm]\]
    Thus, $\chi^\#$ is determined by where it takes $t$. Since $t$ is a unit, it must go to a unit, i.e.
    \[ \chi^\#(t) = cx_1^{m_1}\cdots x_n^{m_n} =: f\]
    with $m_i \in \Z$. Thus, we only need to show $c = 1$. 
    
    We use the Hopf algebra structure. 
    \begin{align*}
        \Delta(f)(g, h) &= f(gh) \\
        &= \chi(gh) \\
        &= \chi(g)\chi(h) 
    \end{align*}
    Thus, $f(gh) = f(g)f(h)$ for all $g, h \in G$. Thus, $f$ is a group homomorphism and $\Delta(f) = f \otimes f$. Thus,
    \begin{align*}
        \Delta(f) &= \Delta(cx_1^{m_1}\cdots x_n^{m_n}) \\
        &= c\Delta(x_1^{m_1}\cdots x_n^{m_n})
    \end{align*}
    However, on the other hand, $\Delta$ is a $k$-algebra map, thus, 
    \begin{align*}
        \Delta(f) = f \otimes f = cx_1^{m_1}\cdots x_n^{m_n} \otimes cx_1^{m_1}\cdots x_n^{m_n} = c^2\Delta(x_1^{m_1}\cdots x_n^{m_n})
    \end{align*}
    Thus, $c^2 = c$ thus $c =1$.  

    To complete the proof, show all of these are realized. Not so hard. 
\end{proof}

\begin{corollary}
    \[ \Hom_{GV}(\G_m^r, \G_m^r) \cong \Mat_{r\times n}(\Z)\]
    That is, if $\phi: \G_m^n \to \G_m^r$ is a group variety map,
    \[ \phi(t_1, \cdots, t_n) = \left(\prod_{i=1}^n t_i^{a_{1i}}, \ldots, \prod_{i=1}^n t_i^{a_{ni}}\right)\]
    That is, maps of tori are monomial maps. 
\end{corollary}
\begin{proof}
    Composing with the $i$th projection gives a character, 
    \[ \G_m^n \to \G_m^r \to \G_m\]
\end{proof}

\begin{corollary}
    \[ \Aut(\G_m^n) \cong \GL_n(\Z)\]
\end{corollary}

\begin{definition}
    Let $T$ be an algebraic torus. The character lattice of $T$ is
    \[ X^*(T) = \Hom_{GV}(T, \G_m) \]
    We showed this is a lattice of rank $n = \dim(T)$, where a lattice if a finitely generated free abelian group.  
\end{definition}

Abstractly, $X^\times(T) \cong \Z^n$ but we write $X^*(T)$ multiplicatively but $\Z^n$ additively. 

\begin{definition}
    We introduce the following notational short-hand: 
    \[ M = X^*(T)\]
    This is also the regular functions on the torus.
\end{definition}


For $\G_m^n$, we have 
\begin{enumerate}
    \item $k[\G_m^n] \cong k[x_1^\pm, \ldots, x_n^\pm]$.
    \item $\Hom_{GV}(\G_m^n, \G_m) \cong \{ \text{ Laurent mons. }\} \cong \Z^n$
\end{enumerate}
Thus, $k[\G_m^n] \cong k[\Z^n]$. Moreover,
\[ k[\Z^n] \cong \bigoplus_{m \in \Z^n} k \cdot \chi^m \]
where $\chi^m \cdot \chi^n = \chi^{m+n}$. 

Thus we are able to identify regular functions on the torus $\G_m^n$ with sums of characters with a direct sum decomposition. 

\begin{definition}
    If $A$ is a finitely generated abelian group its group algebra 
    \[ k[A] \cong \bigoplus_{a \in A} k\chi^a \]
    with $\chi^\alpha \cdot \chi^\beta = \chi^{\alpha + \beta}$. 
\end{definition}

\begin{theorem}
    Let $T$ be an $n$-dimensional torus. Fix $m_1, \cdots, m_n$ a basis for $M$. 
    \begin{enumerate}
        \item Viewing $m_1, \cdots, m_n$ as regular functions on $T$ there is a morphism, 
        \[ T \to^{(m_1, \ldots, m_n)} \G_m^n\]
        is an isomorphism of group varieties. 
        \item There is an isomorphism of commutative Hopf $k$-algebras, 
        \begin{align*}
            k[M] &\to^\sim k[T] \\
            \chi^m &\mapsto m
        \end{align*}
    \end{enumerate}
\end{theorem}

Motto: A torus is recovered from its $M$ lattice. 

Where are we heading with this? Say we have $X$ affine with $T \subset X$ a torus. Then, we get a map, 
\[ k[X] \to k[T] \]
\begin{corollary}
    \[ (k[T])^\times \cong \{ c\chi^m : c \in k^\times, m \in M\}\]
    That is the set of invertible regular functions on $T$ are the characters. 
\end{corollary}

\begin{proof}
    Let $e_1, \ldots, e_n$ be the standard basis for $\Z^n = X^*(\G_m^n)$. 
    \[ e_i(t_1, \ldots, e_n) = t_i\]
    Since $T$ is a torus, we may fix an isomorphism 
    \[ \alpha: T \to \G_m^n\]
    This induces an isomorphism of rings, 
    \[ \alpha^\#: k[\G_m^n] \to k[T]\]
    which is an isomorphism of character lattices contained in these. 
    
    Define $u_i = (\alpha^\#)^{-1}(m_i) \in X^*(\G_m^n)$. Since $\alpha^\#$ is and isomorphism and $m_i$ are a basis, we have $u_1, \cdots, u_n$ is a basis for $X^*(\G_m^n) \cong \Z^n$. 

    Now we have two bases given by the $e_i$ and the $u_i$ for $\Z^n$. Thus ther exists $A \in \GL_n(\Z)$ taking $e_i \mapsto u_i$. 

    Then $A$ is a (monomial) automorphism of $\mu_A: \G_m^n \to^\sim \G_m^n$ with the property that $\mu^\#_A(e_i) = u_i$. 

    Now consider,
    \[ \xymatrix{ T \ar[r]^\sim_a \ar[rd]^\Psi & \G_m^n \ar[d]^{\mu_A} \\ 
    & \G_m^n }\]
    We want to show that this diagram commutes. We check this on coordinate rings. Dualizing this picture, we get, 
    \[ \xymatrix{ k[T] & k[\G_m^n] \ar[l]^\sim_{a^\#}  \\ 
    & k[\G_m^n] \ar[u]_{\mu_A} \ar[ul]^{\Psi^\#}  }\]

    It is enough to check this on $e_1, \cdots, e_n$. We have, 
    \begin{align*}
        (\mu_A \circ \alpha)^\#(e_i) &= \alpha^\#(\mu^\#_A(e_i)) \\ 
        &= \alpha^\#(u_i) \\
        &= m_i \\
        &= \Psi^\#(e_i)
    \end{align*}

    For the second part, we know, 
    \begin{align*}
        k[x_1^\pm, \cdots, x_n^\pm]  &\to k[M] \\
        x_i &\mapsto \chi^{m_i}
    \end{align*}
    Argument similar to before show this is an isomorphism and $k[x_1^\pm, \cdots, x_n^\pm] \cong k[T]$. 
\end{proof}


Start of class 4/9. 

Standing assumption $k = \overline{k}$. 

Recall, a torus is a group variety $T$ such that, 
\[ T \cong \G_m^n = (k^\times)^n\]

There can be more than one group structures on a variety. 
\begin{example}
    $X = \G_m \times \A^1$. First consider the group action, 
    \[ (t, x) \cdot (s, y) = (ts, x+y) \]
    Secondly, the group structure, 
    \[ (t, x) \star (s,y) = (ts, x+ty) \]
    Hopefully, these are $2$ distinct group structures on a variety. 
\end{example}
It isn't necessarily true that two group varieties being abstractly isomorphic as varieties and as groups means they are isomorphic as group varieties. 


Further, recall, the character lattice, 
\[ M = X^\times(T) = \Hom_{GV}(T, \G_m)\]
and that, 
\[ k[T] \cong k[M] \cong \bigoplus_{m \in M} k\chi^m\]

Now, we do new stuff. 
\begin{definition}
    A one parameter subgroup of a group variety $G$ is a group variety homomorphism, 
    \[ \lambda: \G_m \to G\]
    The set of these is $\Hom_{GV}(\G_m, G)$. 
\end{definition}

\begin{lemma}
    \[ \Hom_{GV}(\G_m, \G_m^n) \cong \Z^n \]
\end{lemma}
\begin{proof}
    Every map of standard tori is monomial. We know that $\lambda: \G_m \to \G_m^n$ is the same as giving $\lambda^\#: k[x_1^\pm, \cdots, x_n^\pm] \to k[t^\pm]$ and we have complete freedom for where every variable goes.     
\end{proof}

We define the following notation. The co-character lattice of $T$ is, 
\[ N := X_*(T) := \Hom_{GV}(\G_m, T)\]
and we have $\rk(N) = \dim(X)$. 

For $u \in N$, we normally write, 
\[ \lambda_u: \G_m \to T\]
for the corresponding $m$. 

\begin{example}
    Consider the torus $X = \G_m^2$. Take, $u_1 = (1, -1)$ and $u_2 = (0, 1)$, and $u_3 = (-2, -2)$, $u_4 = (0, 0)$. These correspond to maps $\G_m \to \G_m^2$. These maps are, 
    \[ u_1(t) = (t, t^{-1}), \qquad u_2(t) = (t^0, t^1), \qquad u_3(t) = (t^{-2}, t^{-2}), \qquad u_4(t) = (0, 0)\]
    These can be drawn on the plane. We should also consider what point is the limit as $t \to 0$. 
\end{example}

Fix $m \in M$ and $u \in N$. We take $\chi^m: T \to \G_m$ and $\lambda_u: \G_m \to T$. Now we have, 
\[ \G_m \to^{\lambda_u} T \to^{\chi^m} \G_m\]
The composition is $t \mapsto t^a$ for some unique $\alpha$ in $\Z$. This defines a pairing.
 
\begin{definition}
    For a torus $T$, there is a pairing, 
    \[ \langle, \rangle: M \times N \to \Z \]
    By $\langle m, n \rangle = a \in \Z$ such that $\chi^m \circ \lambda_u = t^a$. 
\end{definition}

\begin{example}
    Let $T = \G_m^n$. Let $M = \Z^n$ and $N = \Z^n$. Then, a choice of $m$ and $n$ is the choice of a tuples $(m_i)$ and $(u_i)$ in $\Z^n$. Then, 
    \[ \lambda_u: t \mapsto (t^{u_i})\]
    and
    \[ \chi^m(x_1, \cdots, x_n) \to \prod_i x_i^{m_i}\]
    Overall, we get, 
    \[ (t^{u_1}, \cdots, t^{u_n}) \mapsto t^{\langle u, m \rangle}\]
    That is, 
    \[ \langle m, u \rangle = m \cdot u\]
\end{example}

\begin{definition}
    The pairing
    \[ \langle \cdot, \cdot \rangle : M \times N \to \Z\]
    is perfect if and only if $\forall m \neq 0 \in M$, there exists $n \in N$ such that $\langle m, n \rangle \neq 0$. Equivalently, it induces an isomorphism, 
    \[ \Hom_\Z(M, \Z) \cong N \qquad \Hom_\Z(N, \Z) \cong M\]
\end{definition}

\begin{theorem}
    If $T$ is a torus, the pairing $\langle \cdot , \cdot \rangle: M \times N \to \Z$ is perfect. 
\end{theorem}

Thus, we have the following maps, 
\begin{align*}
    T &\mapsto X^*(T) \\
    \{k-\text{tori}\} &\mapsto \{\text{lattice}\} \\
    T &\mapsto X_*(T)
\end{align*}
We want a map, 
\[ \{\text{lattices}\} \mapsto \{\text{tori}\}\]

We create this as follows. 

Let $M = \Hom_\Z(N, \Z)$. $k[M]$ is a finitely generateed reduced $k$-algebra. Thus, $T_N$ is the torus that corresponds to $k[M]$. 

\begin{theorem}
    Let $N$ and $N'$ be lattices. If $\phi: N \to N'$ is a homomorphism, there is a torus homomorphism $f_\phi: T_N \to T_{N'}$. This is given on coordinate rings by
    \begin{align*}
        f_\phi^\#: k[T_{N'}] &\to k[T_N] \\
        \chi^{m'} &\mapsto  \chi^{\phi^\vee(m')}
    \end{align*}
    where $\phi^\vee: M' \to M$ with $M'$ dual of $N'$ and $M$ dual to $N$. 

    Moreover, all morphisms $T_N \to T_{N'}$ arise this way. That is, 
    \[ \Hom_{GV}(T_N, T_{N'}) \cong \Hom_\Z(N, N')) \cong \Hom_\Z(M', M) \]
\end{theorem}

\begin{theorem}
    There is an equivalence of categories between $k$-tori and lattices given by co-characters $X_*(T)$ and $T \mapsto T_N$. Together these functors give, 
    \begin{align*}
        &\{\text{lattices}\} \to^\vee \{\text{lattices}\} \to^{k[-]} k-\text{alg} \to^{\Spec} \text{tori} \\
        &N \mapsto M \mapsto k[M] \mapsto \text{tori}
    \end{align*}
\end{theorem}

\begin{example}
    Suppose we have: column $\phi = (2,1)$ from $\Z \to \Z^2$. The dual of this is $\Z^2 \to \Z$ given by row $\phi^\vee = (2, 1)$. Then, we get, 
    \begin{align*}
        k[\G_m^2] &\to k[\G_m] \\
        x &\mapsto t^2 \\
        y &\mapsto t
    \end{align*}
    and 
    \[ \G_m \to \G_m^2, \qquad t \mapsto (t^2, t) \]
\end{example}

\begin{proposition}[Smith Normal Form for Tori]
    If $\phi: N \to N'$ be a lattice map and $f_\phi: T_N \to T_{N'}$ be the induced map on tori. Then there exists bases $\{e_i\}$ and $\{e_i'\}$ of $N$ and $N'$ respectively such that 
    \begin{align*}
        \phi(e_i) = \begin{cases}
            d_ie_i' \qquad 1 \leq i \leq r \\
            0 \qquad \text{otherwise}
        \end{cases}
    \end{align*}
    where $r = \rk(\phi)$, $d_i \in \Z$ and $d_i | d_{i+1}$. 

    Thus, up to automorphisms of the tori, we know that, 
    \[ f_\phi(t_1, \cdots, t_n) = (t_1^{d_1}, \cdots, t_r^{d_r}, 1, \cdots, 1)\]
\end{proposition}

\begin{corollary}
    If $\phi: T \to T'$ is a map of tori then $\img(\phi) \subset T'$ is a subtori. 
\end{corollary}

\begin{proof}
    Up to automorphism, $\img(\phi) \cong \{(t_1, \cdots, t_r, 1, \cdots, 1) | t_i \in \G_m\}$. We can take $d$th roots to ignore the $d_i$. 
\end{proof}

\begin{exercise}
    Consider $\Z^3 \to \Z^4$ given by the matrix, 
    \begin{align*}
        \begin{pmatrix}
            1 & 1 & 0 \\ 
            1 & -1 & 0 \\
            0 & 0 & 2 \\
            0 & 0 & 0
        \end{pmatrix}
    \end{align*}
    The smith normal for is, 
    \[ 
        \begin{pmatrix}
            1 & 0 & 0 \\ 
            0 & 2 & 0 \\
            0 & 0 & 2 \\
            0 & 0 & 0
        \end{pmatrix}
    \]
    This gives us a map of tori, 
    \[ f_\phi(x_1, x_2, x_3) \to (x_1, x_2^2, x_3^2, 1)\]
\end{exercise}

\begin{corollary}
    With $f_\phi: T_N \to T_{N'}$, the following are equivalent, 
    \begin{enumerate}
        \item $f_\phi$ is surjective
        \item $\rk(\phi) = \rk(N')$
        \item $\coker(\phi)$ finite
        \item $\phi^\vee$ injective
    \end{enumerate}
    and similarly, 
    \begin{enumerate}
        \item $f_\phi$ is a closed embedding
        \item $\phi^\vee$ is surjective
        \item $\phi$ injective and $\phi(N) \subset N'$ saturated. 
    \end{enumerate}
\end{corollary}

\begin{definition}
    Let $L' \subseteq L$ be lattices. $L'$ is saturated in $L$ if and only if $mv \in L'$ for $m > 0$, $v \in L$ implies $v \in L'$. 
\end{definition}

\begin{lemma}
    $L' \subset L$ saturated iff $L/L'$ free. 
\end{lemma}

\begin{lemma}
    Let $G$ be an affine group variety. If $\chi_1, \cdots, \chi_n: G \to \G_m$ are distinct characters then they are linearly indepdendent over $k$ as elements in $k[G]$. 
\end{lemma}

\begin{proof}
    Suppose not. Choose a minimal length relation $\psi: G \to k$ given by $\sum_i a_i\chi_i = 0$. with $a_i \in k^\times$. $\Psi: G \to k$. Pick $g \in G$. Then, 
    \begin{align*}
        G &\to G \to k \\
        h &\mapsto gh \mapsto \psi(gh) 
    \end{align*}
    is a regular function. 

    Then, 
    \begin{align*}
        \psi(gh) &= (\sum_i a_i \chi_i)(gh) \\
        &= \sum_i a_i\chi_i(gh) \\
        &= \sum_i a_i \chi_i(g)\chi_i(h) \\
        &= 0
    \end{align*}
    Lets substract $a_1\chi_1(g)\Psi(-)$. Then, 
    \begin{align*}
        0 &= \Psi_g(-) - a_1\chi_1\Psi(-) \\
        &= \sum_{i} a_i\chi_i(g)\chi_i(-) - \sum_i \chi_1(g)a_i\chi_i(-) \\
        &= a_2(\chi_2(g) - \chi(g))\chi_2(-) + \cdots + a_r(\chi_r(g) - \chi_r(g))\chi_r(-)
    \end{align*} 
    Since $\chi_1(g) \neq 0$, this gives us a relation that is smaller. 
\end{proof}

\begin{definition}
    Let $N$ be a lattice with $M$ its dual so that $k[T_N] \cong k[M]$. Let $H \subset T_N$ be a closed group subvariety. 
    \[ L_H = \{ m \in M | \chi^m|_H = 1\}\]
    and 
    \[ I_H = \langle \chi^l -1 | l \in L_H \rangle \]
\end{definition}

\begin{theorem}
    With notation as before, if $H \subset T_N$ is a closed subvariety group then 
    \begin{enumerate}
        \item $\I(H) = I_H$
        \item $k[H] = k[M]/I_H \cong k[M/L_H]$
    \end{enumerate}
\end{theorem}

\begin{example}
    Let $N = \Z^2$, $k[\G_m^2] \cong k[x^\pm, y^\pm]$, $x = \chi^{(1, 0)}$, $y = \chi^{(0, 1)}$. Then, 
    \begin{align*}
        L &= \Z\langle 1, 1 \rangle  = \{ m(1,1) | m \in \Z \}\subset M \cong \Z^2 \\
        I_L &= \langle \chi^{(m, m)} - 1 | m \in \Z \rangle = \langle xy-1 \rangle \\
        H &= \V(I_L) = \{(x,y) \in (k^\times)^2 | xy = 1\} \\
        k[H] &\cong k[x^\pm, y^\pm]/\langle xy-1 \rangle \cong k[x^\pm]
    \end{align*}
\end{example}

\begin{example}
    Same setup. 
    \begin{align*}
        L &= \Z(2,0) \subset \Z^2 \\
        I_L &= \langle x^2-1\rangle \\
        H &= \V(I_L) = \{ (x,y) \in (k^\times)^2 | x^2 = 1\} \\
        &= \{(1,y) | y \in k^\times\} \cup \{(-1,y) | y \in k^\times\} \\
        &\cong \mu_2 \times \G_m
    \end{align*}
    Then, $\Z^2/M \cong \Z \oplus \Z/2\Z$ is not saturated. 
\end{example}

[Day Begin: 4/21]
\begin{corollary}
    If $H \subset T_N$ is connected closed group subvariety, then $H$ is a torus. 
\end{corollary}
\begin{proof}[Proof of corollary]
    Note that the group $H$ acts on itself via translation and since $H$ is connected, $H$ is irreducible. This implies $k[H]$ is a domain. Thus, $k[M/L_H]$ is also a domain. This only happens if $M/L_H$ is a lattice. Thus, this lattice comes from a torus, i.e. $H$ is a torus. 
\end{proof}

\begin{proof}[Proof of Theorem]
    $I_H \subset \I(H)$ is clear. For the other inclusion, take $f = \sum_{m} a_m\chi^m \in \I(H)$. Since $f \in \I(H)$, we know $f|_H = 0$. 

    As an aside, we note the following. For $\chi^m, \chi^{m'} \in k[T]$ we have $\chi^m|_H = \chi^{m'}|_H$ if and only if $\chi^{m-m'}|_H = 1$. To see this, consider, recalling that we are in a domain,
    \begin{align*}
        \chi^m|_H = \chi^{m'}|_H\chi^{m-m'}|_H = \chi^{m'}|_H
    \end{align*}
    
    Then, this means, $\chi^{m}|_H = \chi^m|_H \iff m-m' \in L_H$. 

    Let $\CC$ be a set of cosets for $M/L_H$ and for $C \in \CC$ pick representative $m_c$. Then, 
    \begin{align*}
        f|_H &= \sum_m a_m(\chi^m|_H) \\ 
             &= \sum_{C \in \CC} \sum_{m \in C} a_m \chi^{m_c}|_H
    \end{align*}
    Since $C$ are distinct cosets, we know that, $\chi^{m_c}|_H \neq \chi^{m_c'}|_H$. 

    \begin{align*}
        f|_H = \sum_{C \in \CC} \sum_{m \in C} \chi^{m_C}|_H = 0
    \end{align*}
    Since characters are linearly independent, 
    \[ \implies \sum_{m \in C} a_m = 0 \qquad \forall C \in \CC\]
    Then, 
    \begin{align*}
        &\sum_{m \in C} a_m\chi^{m_c} = 0  \\
        \implies& \sum_{m \in C}a_m\chi^m - \sum_{m\in C}a_m\chi^{m_C} = \sum_{m\in C} a_m(\chi^m-\chi^{m_C})
    \end{align*}
    If $m$ and $m_C$ are in the same coset, then $\chi^{m} - \chi^{m_C} \in I_H$ because $\chi^{m-m_C}-1 \in I_H$. 

    We will say the 2nd statement of the theorem is clear.
\end{proof}

\begin{definition}
    A topological space $X$ is irreducible if and only if any of the following are true: 
    \begin{enumerate}
        \item If $X = V_1 \cup V_2$ with $V_i$ closed and non-empty, then $V_i = X$ for some $i$. 
        \item If $U_1, U_2 \subset X$ are open and non-empty, then $U_1 \cap U_w \neq \emptyset$. 
        \item Every non-empty open set is dense. 
    \end{enumerate}    
\end{definition}

\begin{lemma}
    An affine variety $X$ is irreducible iff $k[X]$ is a domain iff $\I(X)$ is prime. 
\end{lemma}
\begin{corollary}
    \begin{enumerate}
        \item The subtori of $T_N$ are in bijection with saturated sublattices of $M$. The maps are $H \mapsto L_H$ and $L \mapsto k[M/L]$. 
        \item The subtori of $T_N$ is in bijection with saturated sublattices of $N$. 
        The maps are: take $N' \subset N$, map to $(N')^\perp = \{m \in M : \langle m, u\rangle = 0 \, \forall u \in N'\}$. This is satured if $N'$ is saturated. Then take the torus $\V(I_{(N')^\perp})$.  
    \end{enumerate}
\end{corollary}

\begin{example}
    Let $N = \Z^2$ and $N' = \Z\langle 1, 1\rangle$. Then, 
    \begin{align*}
        (N')^\perp = \Z\langle 1, -1\rangle \subseteq M \\
        I_{(N')^\perp} = \langle xy^{-1} -1\rangle 
    \end{align*}
    is the diagonal torus.
\end{example}

\begin{lemma}
    If $N' \subset N$ is a sublattice. Then, $T_N/T_{N'} \cong T_{N/N'}$. 
\end{lemma}

\begin{example}
    Let $N = \Z^{n+1}$ and $N' = \Z\langle 1, \cdots, 1\rangle$. Then, 
    \begin{align*}
        \Delta\G_m \subset \G_m^{n+1} \\
        \G_m^{n+1}/\Delta \G_m \cong T_{\Z^{n+1}/\langle 1, \cdots, 1\rangle}
    \end{align*}
\end{example}


\section{Affine Toric Varieties}
\begin{definition}
    Let $A$ be any finitely generated abelian group. Then $D(A) := \Spec(k[A])$ where $k[A] =\bigoplus_{\alpha \in A} k\chi^\alpha$ with multiplication given by $\chi^a\chi^{b}= \chi^{a+b}$ and $\chi^0 = 1$. This is the diagonal group scheme associated to $A$. 
\end{definition}

\begin{definition}
    If $R$ is a ring and $A$ is an abelian group, then an $A$-grading on $R$ is an isomorphism of abelian groups $R \cong \bigoplus_{a \in A} R_a$ such that $R_bR_b \subset R_{a+b}$. 
\end{definition}

\begin{definition}
        If $G$ is a group variety and $X$ a variety, an algebraic action of $G$ on $X$ is a morphism $G \times X \to X$. 
\end{definition}

\begin{definition}
    If $A$ is an abelian group and $R$ is a ring. A $k[A]$ coaction on $R$ is map, 
    \[ R \to R \otimes k[A]\]
\end{definition}

\begin{theorem}
    Let $A$ be a finitely generated abelian group and $X$ an affine variety over $k$. Set $R = k[x]$ and $G = D(A)$. The following are equivalent: 
    \begin{enumerate}
        \item An $A$-grading on $R$
        \item An algebraic action on $G$ on $X$
        \item $k[A]$-coaction on $R$. 
    \end{enumerate}
\end{theorem}
\begin{proof}
    Given $R \cong \bigoplus R_a$ take the map $R \to R \otimes k[A]$ by sending $r \mapsto r \otimes \chi^{\deg(r)}$. Alternatively, if we take $\rho: R \to R\otimes k[A]$ then $R_a = \{r \in R | \rho(r) = r \otimes \chi^\alpha \}$. 
\end{proof}

\begin{definition}
    An affine toric variety is an affine variety $X$ with an open dence torus $T \subset X$ such that the action extends to an action $T \times X \to X$. 
\end{definition}

We think of $k[X]$ as the ``characters of $T$ that do not blow-up on $X \setminus T$". We know that $k[X] \to k[T]$. We also know $k[T] \cong k[M]$. If two characters dont blow up, neither does their product. The $\chi^0$ does not blow up either. This means,
\[k [x] = k\{\chi^m | m \in S'\}\]

\begin{definition}
    A semigroup is a set $S$ together with an associative, commutative, binary operation $+$ that has an identity element $0$. Some people call these monoid. 
\end{definition}

\begin{example}
    Take $\N = \{0, 1, \cdots\}$. This is a semi-group. 
\end{example}

\begin{example}
    Take $\Z/2\Z$ is a semi-group that does not embed in a lattice (it has torsion). 
\end{example}

\begin{example}
    $S = \{0, 1, \infty\}$ with typical multiplication does not cancel so doesn't embed into a lattice. 
\end{example}

\begin{definition}
    An affine semigroup is a finitely generated semigroup that embeds into a lattice. 
\end{definition}

Given $m \in \N$ and a semigroup $S$ with $x \in S$, we define $mx = \underbrace{x+\ldots+x}_{m \text{ times}}$. Given $A \subset S$, 
\[ \N(A) = \left\{ \sum_{i=1}^n m_is_i | m_i \in \N, s_i \in A, n > 0 \right\}\]

\begin{definition}
    A semigroup $S$ is finitely generated if $S = \N\{m_1, \cdots, m_t\}$. 
\end{definition}

If $S$ is an affine semigroup, $S \subset M$ with $M$ a lattice, then, 
\[ \Z S = \left\{\sum_{i = 1}^n m_is_i | m_i \in \Z, s_i \in S, n > 0\right\} \subset M\]

\begin{example}
    If we take $S = \N(1,1) \subset \Z^2$. Then $\Z S$ is $\Z(1,1)$. 
\end{example}

\begin{definition}
    If $S \subset M$ is an affine semigroup. The semigroup ring is:
    \[ k[S] = \bigoplus_{m \in S} k\chi^m \subset k[M]\]
    where multiplicated is defined in the usual manner. 
\end{definition}

\begin{example}
    Let $S = \N^t \subset \Z^t = M$. Then, 
    \[ k[S] = k[\chi^{e_1}, \ldots, \chi^{e_t}] = k[x_1, \ldots, x_n] \subset k[x_1^\pm, \ldots, x_t^\pm ] \] 
\end{example}

\begin{example}
    Let $S = \N\{2, 3\} \subset \Z$. This does not contain $1$, i.e. it not saturated. Note, 
    \[ k[S] \cong k[t^2, t^3]\]
    We will see that singularities correspond to non-saturation. 
\end{example}

\end{document}