\documentclass[12pt]{article}

\include{../style}

\begin{document}

\input{title}

\begin{problem}{1}
    \begin{enumerate}
        \item[(a)] Check the equivalence between the two definitions of the Hodge structure of weight $k$ given in class. 
        \item[(b)] Check the a morphism Hodge structures is strict for the Hodge filtration. 
        \item[(c)] Show that the kernel, cokernel, and image of a morphism of Hodge structures are Hodge structures.
        \item[(d)] Let $\phi: X \to Y$ a surjective holomorphic map of complex compact manifolds such that $X$ is k\"ahlerian. Show that $\phi^*$ is injective.
    \end{enumerate}
\end{problem}
\begin{solution}
    \bbni
    \begin{enumerate}
        \item[(a)] First assume that we have filtration of $V_\C$:
        \[ 0 = F^{k+1} \subset F^k V_\C \subset F^{n-1} V_\C \subset \cdots \subset F^0 V_\C = V_\C\]
        that satisfies the condition: 
        \[ F^p V_\C \oplus \overline{F^{k-p+1} V_\C } = V_\C\]
        Then, we define: 
        \[ H^{p, q} = F^p V_\C \cap \overline{F^q V_\C}  \]
        Clearly, with this definition, we have: 
        \begin{align*}
            \overline{H^{p, q}} &= \overline{F^p V_\C \cap \overline{F^q V_\C}} \\
            &= \overline{F^p V_\C} \cap F^q V_\C \\
            &= H^{q, p}
        \end{align*}
        We will show that: 
        \begin{align*}
            F^{i} V  = \bigoplus_{p \geq i} H^{p, k-p}
        \end{align*}
        Notice that: 
        \begin{align*}
            F^{i} V_\C &= F^{i} V_\C \cap V_\C \\
            &= F^{i} V_\C \cap (F^{i+1} V_\C \oplus \overline{F^{k-(i+1)+1} V_\C }) \\
            &= F^{i} V_\C \cap (F^{i+1} V_\C \oplus \overline{F^{k-i} V_\C }) \\
            &= (F^{i} V_\C \cap F^{i+1} V_\C)  \oplus (F^{i} V_\C \cap \overline{F^{k-i} V_\C}) \\
            &= F^{i+1} V_\C  \, \oplus (F^{i} V_\C \cap \overline{F^{k-i} V_\C }) \\ 
            &= F^{i+1} V_\C \oplus H_{i, k-1} \\
            &= \bigoplus_{p \geq i} H^{p, k-p}
        \end{align*}
        Where the third equality uses the fact that $A \cap (B \oplus C) = A \cap B \oplus A \cap C$ if $B \subseteq A$ as if $a = b + c \in A \cap (B \oplus C)$ ($a \in A, b \in B, c \in C$), then since $b \in B \subset A$, we have $a-b = c \in A$. Thus, $b \in A \cap B$ and $c \in A \cap C$ and $A \cap (B \oplus C) \subseteq A \cap B \oplus A \cap C$. The other inclusion is clear. \bbni 
        Thus, noting the result for $i = 0$, we have recovered the first definition of a Hodge structure of weight $k$. \bbni
        Now, assume that we have a decomposition of $V_\C$ into the direct sum of the $H^{p, q}$:
        \[ V_\C = \bigoplus_{p + q = k} H^{p, q}\]
        with $H^{p, q} = \overline{H^{q, p}}$. Then, we define the filtration similarly:
        \[ F^p V_\C = \bigoplus_{i \geq p} H^{i, k-i}\]
        Then, we have that: 
        \begin{align*}
            F^p V_\C \oplus \overline{F^{k-p+1} V_\C} &= \bigoplus_{i \geq p} H^{i, k-i} \oplus \overline{\bigoplus_{j \geq k-p+1} H^{j, k-j}} \\
            &= \bigoplus_{i \geq p} H^{i, k-i} \oplus \bigoplus_{j \geq k-p+1} H^{k-j, j} \\
            &= \bigoplus_{i \geq p} H^{i, k-i} \oplus \bigoplus_{j' \leq p-1} H^{j', k-j'} \\
            &= \bigoplus_{i \geq 0} H^{i, k-i}  \\
            &= V_\C
        \end{align*}
        Thus, we have recovered the second definition of a Hodge structure of weight $k$.
        \item[(b)] Recall the defnition of a morphism of Hodge structures. Let $V_\Z$ and $V'_\Z$ be two hodge structures of weight $k$ and $k+2r$. Then a morphism of Hodge structures of type $(r, r)$ is a group morphism $\phi$ whose $\C$-linear extension (which we will also call $\phi$ for this part) satisfies: 
        \[ \phi(V^{p,q}) \subseteq {V'}^{p+r, q+r} \iff \phi(F^p V) \subset F^{p+r} V'\]
        We need to show that this is strict for the Hodge filtration, i.e.
        \[ \img(\phi) \cap F^{p+r} V' = \phi(F^p V)\]
        Let $\alpha \in \img(\phi) \cap F^{p+r} V'$. Then, there exists $\beta \in V$ such that $\phi(\beta) = \alpha$. Then, using the decomposition of $V$, we can write: 
        \begin{align*}
            \alpha &= \phi(\beta) \\
            &= \phi\left(\sum_{i+j = k} \beta^{i,j}\right) \\
            &= \sum_{i+j = k} \phi(\beta^{i,j}) 
        \end{align*}
        Then, each $\phi(\beta^{i,j})$ is of type $(i+r, j+r)$. Then, if $i < p$, note that $\phi(\beta^{i, j}) \in {V'}^{i+r, j+r} \cap F^{p+r}$. But, as noted from the previous problem, we have:
        \[ F^{p+r} V' = \bigoplus_{i \geq p+r} H^{i, k-i} \]
        Thus, we have that $\phi(\beta^{i,j}) = 0$ for $i < p$. Thus, we can write:
        \begin{align*}
            \alpha &= \sum_{i \geq p} \phi(\beta^{i,k-i}) \in F^{p+r} V' 
        \end{align*}
        noting the decomposition for $F^{p+r} V'$ from the previous problem and that $\phi(\beta^{i,j}) \in {V'}^{i+r, j+r}$ (as noted before). Thus, we have that:
        \[ \img(\phi) \cap F^{p+r}V' \subseteq \phi(F^{p}V) \]
        The other direction is implied in the definition of a Hodge structure morphism. 
        \item[(c)] Let $\phi: V_\Z \to {V'}_\Z$ be a morphism of Hodge structures of type $(r, r)$, where $V$ is of weight $k$ and $V'$ is of weight $k+2r$. We first prove that $\img(\phi)$ and $\ker(\phi)$ have natural Hodge structures. \bbni
        For $\img(\phi)$, first note that:
        \[ \img(\phi_\C) = \img(\phi) \otimes_\Z \C \qquad \ker(\phi_\C) = \ker(\phi) \otimes_\Z \C \]
        Thus, we can define the filtration on $\img(\phi_\C)$ by: 
        \[ F^p \img(\phi_\C) := \img(\phi) \cap F^{p} V'_\C \]    
        It is easy to see that these define a decreasing filtration on $\img(\phi)$ and $\ker(\phi)$ by the filtration structures on the codomain and domain. Then, note for $\img(\phi)$ that we have: 
        \begin{align*}
            F^{p} \img(\phi_\C) \oplus \overline{F^{k+2r-p+1} \img(\phi_\C)} 
            &= \img(\phi) \cap F^{p} V'_\C \oplus \overline{\img(\phi) \cap F^{k+2r-p+1} V'_\C} \\
            &= \phi(F^{p-r} V) \oplus \overline{\phi(F^{k+r-p+1} V_\C)} \\
            &= \phi(F^{p-r} V \oplus \overline{F^{k+r-p+1} V_\C}) \\
            &= \phi(V_\C) \\
            &= \img(\phi_\C)
        \end{align*}    
        Thus, $\img(\phi)$ has an Hodge structure of weight $k+2r$ and for $\ker(\phi)$, we note that:
        \[ \ker(\phi_\C) = \bigoplus_{p+q = k} \ker(\phi_\C) \cap V^{p,q}\]
        as the $V^{p, q}$ are disjoint. Let $K^{p, q} = \ker(\phi) \cap V^{p,q}$. Then, we have that: 
        \[ \overline{\ker(\phi_\C) \cap V^{p, q}} = \overline{\ker(\phi_\C)} \cap V^{q, p}\]
        But $\ker(\phi_\C)$ is closed under complex conjugation as $\phi_\C$ is $\C$-linear. Thus, we have shown that:
        \begin{align*}
            \ker(\phi_\C) &= \bigoplus_{p+q = k} K^{p, q}  \qquad K^{p, q} = \overline{K^{q, p}}
        \end{align*}
        Thus, we have that $\ker(\phi_\C)$ is a Hodge structure of weight $k$. \bbni
        Finally, for the cokernel, note that:
        \begin{align*}
            \coker(\phi_\C) &= V'_\C / \img(\phi_\C) \\
            &= (V' \otimes_\Z \C)/(\img(\phi) \otimes_\Z \C) \\
            &= (V'_\C / \img(\phi_\C)) \otimes_\Z \C \\
            &= \coker(\phi) \otimes_\Z \C
        \end{align*}
        Let
        \[ \coker(\phi_\C)^{p,q} = {V'}^{p,q} / \img(\phi)^{p,q}\]
        where $\img(\phi)^{p,q}$ is the $(p,q)$-part of $\img(\phi_\C)$. Then, we have:
        \begin{align*}
            \img(\phi_\C)^{p,q} &= (\img(\phi_\C) \cap F^{p} V'_\C) \cap (\overline{\img(\phi_\C) \cap F^{q} V'_\C}) \\
            &= \img(\phi_\C) \cap {V'}^{p,q} \subseteq {V'}^{p,q}
        \end{align*}
        as the image is closed under complex conjugation. Thus, using these compatible decompositions, we note:  
        \begin{align*}
            \bigoplus_{p+q = k+2r} \coker(\phi_\C)^{p,q} &= \bigoplus_{p+q = k+2r} {V'}^{p,q} / \img(\phi_\C)^{p,q} \\
            &= \left(\bigoplus_{p+q = k+2r} {V'}^{p,q}\right)/ \left(\bigoplus_{p+q = k+2r} \img(\phi_\C)^{p, q}  \right) \\
            &= {V'}_\C / \img(\phi_\C) \\
            &= \coker(\phi_\C)
        \end{align*}
        Moreover, we have that:
        \begin{align*}
            \overline{\coker(\phi_\C)^{p,q}} &= \overline{{V'}^{p,q} / \img(\phi_\C)^{p,q}} \\
            &= {V'}^{q,p} / \img(\phi_\C)^{q,p} \\
            &= \coker(\phi_\C)^{q, p}            
        \end{align*}
        as the quotient map is $\C$-linear, thus respects the complex structure. Thus, we have that $\coker(\phi_\C)$ is a Hodge structure of weight $k+2r$.
        \item[(d)] (I took several hints from the proof in Voisin, and the proof gradually looked more and more like hers). \bbni 
        Note that the pullback is: 
        \[ \phi^*: H^k(Y, \Z) \to H^k(X, \Z)\]
        It suffices to show that $\phi^*$ is injective with $\R$ coefficients. Let $\dim_\C(X) = n$ and $\dim_\C(Y) = m$. Let $\alpha \in H^{2m}(Y, \R)$. Then, we have $\phi^*\alpha \in H^{2m}(X, \R)$. Let $r = n-m > 0$ (as $\phi$ surjective). Then, we have that $\omega^r \wedge \phi^*\alpha \in H^{2n}(X)$ is a top-degree form on $X$, where $\omega$ is the K\"ahler form. Voisin claims that this map is always non-negative, and positive on at least an open set. Thus, the integral:
        \[ \int_X \omega^r \wedge \phi^*\alpha > 0 \]
        Thus, $\phi^* \alpha \geq 0$. We conclude that $\phi^*$ is injective on $H^k(Y, \R)$ using Poincare duality to get a top-form on $Y$, and noticing that the pullback distributes over the cup product (and is, in particular, a ring homomorphism).      
    \end{enumerate}
\end{solution}


\newpage



\begin{problem}{2}
    Let $H_\R$ be a $\R$-vector space, and $H_\C := H_\R \otimes_\R \C$.
    \begin{enumerate}
        \item[(a)] Show that a decomposition
        \[ H_\C = \bigoplus_{p+q=k} H^{p,q} \qquad H^{p,q} = \overline{H^{q,p}}\]
        determines a continous action $\rho: \C^\times \to \text{GL}(H_\C)$ of $\C^\times$ on $H_\C$ given by:
        \[ z \cdot \alpha^{p,q} = z^p\overline{z^q}\alpha^{p,q}\]
        for $\alpha^{p,q} \in H^{p,q}$. Show that this action satisfies: 
        \[ \rho(z) = \overline{\rho(z)}\]  
        where the conjugacy on $GL(H_\C)$ is defined by: 
        \[ \overline{g}(u) = \overline{g(\overline u)}\]
        Show that one also has $\rho(t) = t^k \id$ for $t \in \R^\times$.
    \end{enumerate}
        Conversely, let $\rho: \C^\times \to GL(H_\C)$ be a continous action of $\C^*$ on $H_\C$ satisfying $\rho(t) = t^k \id$ for $t \in \R^*$ and $\rho(z) = \overline{\rho(z)}$. Show that there exists a decomposition of $H_\C$ into the direct sum of the $H^{p,q}$ such that $\rho(z)$ acts as above.
    \begin{enumerate}[resume]
        \item[(b)] Applying the diagonalization theorem for the actions of torsion abelian groups to the torsion points of $\C^*$, show that there exists a decompositon into a direct sum:
        \[ H = \bigoplus_\chi H_\chi\]
        where $\chi$ belongs to the set of characters of $\C^*$ and $\C^*$ acts by $z \to \chi(z)\id$ on $H_\chi$.
        \item[(c)] Show that only the characters $\chi_{p, q}: z \to z^p\overline{z}^q$ with $p+q = k$ appear in the decomposition of $H_\C$.
        \item[(d)] Let $H^{p,q} := H_{\chi_{p,q}}$. Show that $H^{p, q} = \overline{H^{q, p}}$. 
        \item[(e)] Let $V_\Z$ be a Hodge structure of weight $2k$ and $\C^* \to GL(V_\R)$ the corresponding group morphism defined in the previous question. Show that the group of Hodge classes is equal to the group of stable (i.e. fixed up to a scaler) vectors of $V_\Z$ under the action of $\C^*$.
    \end{enumerate}
\end{problem}
\begin{solution}
    \bbni
    Collaboration notice: For parts b) and c), I got hints from Henry.
    \begin{enumerate}
        \item First, note that the map $z \to z^p\overline{z}^q$ is continous as a map from $\C^\times$ to $\C^\times$. Thus, the map $z \to z^p\overline{z}^q\id$ is continous on each factor of the direct sum, thus it is continous by definition of the product/direct sum topology on vector spaces. \bbni
        Next, note that for $\alpha \in H_\C$, we have:
        \begin{align*}
            \overline{\rho(z)}(\alpha^{p, q}) &= \overline{\rho(z)(\overline{\alpha^{p,q}})} \\
            &= \overline{z^p\overline{z}^q \alpha^{q,p}} \\
            &= \overline{z}^p z^q \overline{\alpha^{q,p}} \\
            &= \overline{z}^pz^q \alpha^{p,q} \\
            &= \rho(\overline{z})(\alpha^{p,q})
        \end{align*}
        Finally, if $t \in \R^\times$, we have $t = \overline{t}$, thus, for $\alpha \in H_\C$ with $\alpha \in H_\C$, we have:
        \begin{align*}
            \rho(t)(\alpha^{p,q}) &= t^p\overline{t}^q \alpha^{p,q} \\
            &= t^k \alpha^{p,q}
        \end{align*}
        for all $p+q = k$. Thus, we have that $\rho(t) = t^k \id$ for $t \in \R^\times$. 
        \item I did not know how to do this part. 
        \item First consider some primitive $n$th root of unity $\zeta_n$ (one of them generates the rest). Then, since $\chi$ is a group homomorphism $\C^\times \to \C^\times$, we have:
        \begin{align*}
            \chi(\zeta_n)^n &= \chi(\zeta^n) = \chi(1) = 1
        \end{align*} 
        Thus, $\chi(\zeta_n)$ is a $n$th root of unity, thus is some power of $\zeta_n$, i.e.:
        \[ \chi(\zeta_n) = \zeta_n^m\]
        Since the action is continous and $n$th roots of unity are dense in the unit circle, we conclude that there is a fixed $m$ such that for all $z \in \C^\times$ with $|z| = 1$, we have:
        \[ \chi(z) = z^m\]

        For $z \in \C^\times$, we can write $z = (z\overline z)^{1/2}e^{i\theta}$. Then, we have: 
        \begin{align*}
            \chi(z) &= \chi((z\overline z)^{1/2}e^{i\theta}) \\
            &= \chi(z\overline z)^{1/2}\chi(e^{i\theta}) \\
            &= (z^k\overline z^k)^{1/2}e^{im\theta}
        \end{align*}
        Then (Henry helped with this part), we compute:
        \begin{align*}
            \chi(z) &= (z^{k-m}\overline z^{k-m})^{1/2}(z^m\overline z^m)^{1/2}e^{im\theta} \\
            &= (z^{k-m}\overline z^{k-m})^{1/2}z^m \\
            &= \overline z^{(k-m)/2}z^{(k+m)/2} \\
        \end{align*}
        Thus, we can set $p:= (k+m)/2$ and $q := (k-m)/2$. We only need to show that $p, q \in \Z$. Note that, since $\chi(t) = t^k$ for $t \in \R^\times$,:
        \begin{align*}
            \chi(-1) &= (-1)^k = 1^ke^{im\pi}
        \end{align*}
        Thus, $m \equiv k \pmod 2$. Thus, $p, q \in \Z$ and we finally have:
        \[ \chi(z) = z^p\overline z^q\]
        \item Note that, we are also given:
        \[ \rho(z) = \chi(\overline z)\id = \overline{\chi(z)\id} = \overline{\rho(z)} \]
        Thus, for $\alpha \in H_\C$, let $\alpha^{p,q} \in H^{p,q}$, then, we have:
        \begin{align*}
            \rho(z)(\overline{\alpha^{p,q}}) &= \chi( z)\id(\overline{\alpha^{p, q}})\\
            &= \overline{\chi(z)\id}(\overline{\alpha^{p, q}}) \\
            &= \overline{\chi(z)\id(\alpha^{p,q})} \\
            &= \overline{z^p \overline z^q \id(\alpha^{p, q})} \\
            &= z^q \overline z^p \id(\overline{\alpha^{p,q}})
        \end{align*}
        Thus, $\overline{\alpha^{p,q}} \in H^{q,p}$. As complex conjugation is self-inverse, we get the other inclusion. Thus, we have that $H^{p,q} = \overline{H^{q,p}}$.
        \item Let $\alpha \in V^{n, n} \cap V_\Z$ be a Hodge class. Then, for any $z \in \C^\times$, we have:
        \begin{align*}
            \rho(z)(\alpha) &= z^n\overline{z}^n \alpha \\
            &= |z|^{2n}\alpha
        \end{align*}
        Thus, $\alpha$ is a stable vector under the action of $\C^\times$. Next, let $\alpha \in V_\Z \subset V_\C$ be a stable vector under the action of $\C^\times$. Let $\alpha^{p,q} \in V^{p,q}$. Then, we have:
        \begin{align*}
            \rho(z)(\alpha^{p,q}) &=\sum_{p+q=2k} z^p\overline{z}^q \alpha^{p,q}
        \end{align*}
        Then, if we want all components of $\alpha$ to be scaled by the same scaler, we want $\alpha^{p,q} \ne 0$ for at most one $(p,q)$. Thus, $\alpha = \alpha^{p,q}$ for some $p, q$ such that $p+q = 2k$.
        I do not understand why we also want $z^p\overline{z}^q$ to also be real, but assuming we do want that (why does the definition of the action includes $V_\R$ in place of $V_\C$ in Voisin?), it follows that we want $p = q = k$. Thus, $\alpha$ is a Hodge class. \bbni 
        In general, I used the correction you emailed Henry about, i.e. that $\rho(z) = \overline{\rho(z)}$. This makes part 4) work out. However, I still showed that $\rho(\overline z) = \overline{\rho(z)}$ in part 1). These do not agree. I'm wondering if the definition of conjugation for $GL(H_\C)$ is incorrect.
    \end{enumerate}
\end{solution}
\newpage


\begin{problem}{3}(The Hodge Decomposition for Curves)
    Let $X$ be a compact connected complex curve. We have the differential:
    \[d: \calO_X \to \Omega_X\]
    between the sheaf of homolormphic functions and the sheaf of holomorphic differentials.
    \begin{enumerate}
        \item[(a)] Show that $d$ is surjective with kernel equal to the constant sheaf $\C$. Hence, we have an exact sequence: 
        \[ 0 \to \C \to \calO_X \rightarrow \to \Omega_X \to 0\]
        \item[(b)] Deduce from Serre duality that $H^1(X, \Omega_X) \cong \C$. Deduce from Poincare duality that $H^2(X, \C) = \C$. 
        \item[(c)] Show that $(6.15)$ induces a short exact sequence: 
        \[ 0 \to H^0(X, \Omega_X) \to H^1(X, \C) \to H^1(X, \calO_X) \to 0\]
        \item[(d)] Show that the map which to a holomorphic form $\alpha$ associates the class of $\overline{\alpha}$ in $H^1(X, \calO_X)$ is injective.
        \item[(e)] Deduce from Serre duality that it is also surjective and that we have the decomposiiton: 
        \[ H^1(X, \C) = H^0(X, \Omega_X) \oplus \overline{H^0(X, \Omega_X)}\]
        with 
        \[ \overline{H^0(X, \Omega_X)} \cong H^1(X, \calO_X)\]
    \end{enumerate}

\end{problem}
\begin{solution}
    \bbni 
    \begin{enumerate}
        \item Let $U$ be an open set of $X$. Let $\omega \in \Omega_X(U)$ be a section. Then $\omega = f dz$ in local coordinates. Since holomorphic functions are analytic, they have a primitive locally. Thus, there exists $g \in \calO_X(U)$ such that $dg/dz = f$. Then, we have that $d(g) = f dz = \omega$. Thus, $d$ is surjective. \bbni
        Now let $f \in \calO_X(U)$ such that $df = 0$. Thus, $f$ is locally constant. Since $X$ is compact and connected, $f$ extends to a globally constant function in $\calO_X(X)$. Thus, $\ker(d) = \C$, the constant sheaf. \bbni
        Thus, we have the exact sequence:
        \[ 0 \to \C \to \calO_X \xrightarrow{d} \Omega_X \to 0\]
        \item Recall that Serre duality gives us the isomorphism:
        \[ H^1(X, \Omega_X) \cong H^0(X, \Omega_X^\vee \otimes \Omega_X)^\vee\]
        However, $\Omega_X^\vee \otimes \Omega_X \cong \calO_X$ (by contracting). Thus, we have:
        \[ H^1(X, \Omega_X) \cong H^0(X, \calO_X)^\vee\]
        However, $H^0(X, \calO_X) \cong \C$ as global holomorphic functions on a compact connected surface are constant. Thus, $H^1(X, \Omega_X) \cong H^0(X, \calO_X)^\vee \cong \C$. \bbni
        Recall that Poincare duality gives us the isomorphism:
        \[ H^2(X, \C) \cong H^0(X, \C)^\vee\]
        Similar to before, as $X$ is compact and connected, we have that $H^0(X, \C) \cong \C$. Thus, we have:
        \[ H^2(X, \C) \cong H^0(X, \C)^\vee \cong \C\]
        \item We obtain the long exact sequence in cohomology from the short exact sequence. 
        \begin{align*}
            \to H^0(X, \C) \to H^0(X, \calO_X) \xrightarrow{d} H^0(X, \Omega_X) \to H^1(X, \C) \to \cdots
        \end{align*}
        Note that $H^0(X, \C)$ are the globally constant functions, which are the same as the global holomorphic functions on a compact connected manifold. Thus, the first map is an isomorphism. Thus, $d:H^0(X, \calO_X) \to H^0(X, \Omega_X)$ is $0$. Thus, the sequence becomes:
        \[0 \to H^0(X, \Omega_X) \to H^1(X, \C) \to H^1(X,\calO_X) \to H^1(X, \Omega_X) \to H^2(X, \C) \to  H^2(X, \calO_X) \]
        Then, since $H^2(X, \calO_X) = H^{0,2}(X) = 0$, the last map is $0$. Thus, the map $H^1(X, \Omega_X) \to H^2(X, \C)$ is an isomorphism. Thus, the map before it is $0$, and we get:
        \[0 \to H^0(X, \Omega_X) \to H^1(X, \C) \to H^1(X,\calO_X) \to 0  \]   
        \item Let $\alpha \in H^0(X, \Omega_X)$ be a global holomorphic form. Then, $\overline{\alpha} \in H^1(X, \C)$ is of type $(0, 1)$ (antiholomorphic). If $[\overline{\alpha}] = 0 \in H^1(X, \calO_X)$, then $\overline{\alpha}$ is in $\img(H^0(X, \Omega_X) \to H^1(X, \C))$. But this is an inclusion map (the connecting morphism deals solely with holomorphic objects), thus, we would have $\overline{\alpha} = \beta$ for some global holomorphic form $\beta$. This implies $\alpha = 0$. Thus, the map is injective. 
        \item By Serre duality, we noted that
        \[ H^1(X, \Omega_X) \cong H^0(X, \calO_X)^\vee\]
        Moreover, since these are finite-dimensional vector spaces, the dual has the same dimension as the original space. Thus, 
        \[ \dim(H^1(X, \Omega_X)) = \dim(H^0(X, \calO_X))\]
        Thus, an injective linear map is also surjective. Thus, the map given is an isomorphism. Since taking the complex conjugate is also an isomorphism, we must have that: 
        \[ \overline{H^0(X, \Omega_X)} \cong H^1(X, \calO_X)\]
        Then, also noting that an SES of vector spaces splits, we get: 
        \[ H^1(X, \C) = H^0(X, \Omega_X) \oplus \overline{H^0(X, \Omega_X)}\]
    \end{enumerate}
\end{solution}
\newpage

\end{document}