\documentclass[12pt]{amsart}


\include{../style}


\begin{document}


\input{title}

\section{Background}

\subsection{The Complex Numbers}
Basic vector space structure. Euclidean metric. Definition of functions between complex numbers. Example: $f: z \to \frac{1}{z}$. \\

\begin{proposition}[W 1.7]
    Suppose $D \subset \R^2$ is open and connected and $u: D \subseteq \R^2 \to \R$ is such that $u_x \equiv 0 \equiv u_y$. Then $u$ is constant. 
\end{proposition}

\begin{definition}
    $F: D \subseteq \R^2 \to \R^2$ is differentiable at a interior point $z_0 \in D$ if there is a linear map $T: \R^2 \to \R^2$ such that: 
    \[ \lim_{z \to 0} \frac{1}{||z||} ||F(z+z_0) - F(z_0) -T(z)|| = 0 \]
\end{definition}

\begin{remark}
    If $F(z) = (u(x, y), v(x, y))$ is differentiable at $z_0$, then $u$ and $v$ have first partials at $z_0$ and the matrix of $T$ with respect to the standard basis is:
    \[ [T]_\sigma = \begin{pmatrix}
        u_x(z_0) & u_y(z_0) \\
        v_x(z_0) & v_y(z_0)
    \end{pmatrix}\]
    The converse fails! W Ex. 1.2.2.
\end{remark}


\begin{theorem}[W 1.8]
    Suppose that $F : D \subset \R^2 \to \R^2$ is given by $F(x, y) = (u(x,y), v(x,y))$ and $D_r(z_0) \subset D$. If the first partials of $u$ and $v$ exist in $D$ and are continous at $z_0$ then $F$ is differentiable at $z_0$. 
\end{theorem}

If the partials are defined in the neighborhood of $z_0$, it makes sense to talk about their partials, giving us the 2nd derivatives, i.e. $u_{xx}, u_{xy}, u_{yx}, u_{yy}$. 
\begin{theorem}[W 1.9, Clauraut]
    If $u_{xy}$ and $u_{yx}$ are continous at $z_0$, then $u_{xy} = u_{yx}$. 
\end{theorem} 

Now we want to defined some interesting functions of complex variables. 
\begin{definition}
    We define the complex exponential $exp: \C \to \C$ by: 
        \[ \exp(x+iy) = e^x\cos (y) + ie^x\sin(y)\]
\end{definition}


\begin{proposition}[W 1.16] 
    The exponential has the following properties: 
    \begin{enumerate}
        \item $e^{z+2\pi i} = e^z$. 
        \item $e^{z+w} = e^z \cdot e^w$
        \item $e^{-1} = \frac{1}{e^z}$
        \item $e^z = e^w \iff w = z + 2\pi i k$ for $k \in \Z$. 
    \end{enumerate}
\end{proposition}
\begin{proof}
    Problem 1 on PSet 1.  
\end{proof}

\begin{definition}
    We say $\tau \in \C$ is unimodular if $|z| = 1$. This happens if and only if $z = e^{i\theta}$ when $\theta \in \R$. \\
    If $z \in \C \setminus \{0\}$, then the polar form is:
    \[ z = |z| \frac{z}{|z|} = re^{i\theta}\]
    where $\theta$ is called the argument. We have:
    \[ \arg(z) = \{\theta \in \R : z = |z|e^{i\theta}\}\]
    and if $z = re^{i\theta_0}$ then: 
    \[ \arg(z) = \{\theta_0 + 2\pi k : k \in \Z\}\] 
    Note that $\arg$ is a set-valued function in $\C \setminus \{0\}$. 
\end{definition}

\begin{proposition}[W 1.2.2]
    Let $f(z) = \exp(z)$. Then, $f$ maps $\C$ to $\C \setminus \{0\}$. Then, 
    \[ \{w \in \C : e^w = z\} = \{\ln(|z|) + i\theta : \theta \in \arg(z)\} = \ln(|z|) + i\arg(z) \]
\end{proposition}

\begin{definition}
    If $z \neq 0$, then we define the (set-valued) logarithm:
    \[ \log(z) = \ln(|z|) + i\arg(z)\]
\end{definition}

Now, we need to talk about picking branches to get honest-to-goodness functions. 
\begin{definition}
    Suppose that $f$ is a set-valued function on a set $D$. Then a branch of $f$ is $D$ is a continous function $F: D \to \C$ such that: 
    \[ F(z) \in f(z) \quad \forall z \in \C \]
\end{definition}

\begin{example}
    Let $z \in \C \setminus \{0\}$ then $\exists! \theta \in (-\pi, \pi]$ such that $\theta \in \arg(z)$. Then we can define: 
    \[ \Arg: \C \setminus \{0\}  \to (-\pi, \pi]\]
    such that $\Arg(z) \in arg(z)$. \\
    This has a jump discontinuity on $(-\infty, 0]$ but is continous elsewhere. See W Lemma 1.26.
\end{example}

A branch of $\arg$ in $D$ gives us a branch of the logarithm in $D$. We call: 
\[ \Log(z) = \ln(|z|) + i \Arg(z)\]
the principal branch of log in $D^*$. \\

This is highly non-unique. One thing we would want to show is that there is no cut you can make to get a logarithm continous everywhere. 

\begin{exercise}{1.4.1.}
    Show the following properties for the complex exponential: 
    \begin{enumerate}
        \item $e^{z+2\pi i} = e^z$
        \item $e^{z+w} = e^ze^w$
        \item $e^{z-w} = \frac{e^z}{e^w}$
        \item $e^{-z} = \frac{1}{e^z}$
    \end{enumerate}
\end{exercise}

\begin{exercise}{1.4.8(a).}
    Use $(1.6)$, De Moivre's Formula, and the geometric sum $1+z + \cdots z^n = \frac{z^{n+1}-1}{z-1}$ to prove the following assuming $0 < \theta < 2\pi$. 
    \[ 1 + \cos(\theta) + \cdots + \cos(n\theta) = \frac{1}{2} + \frac{\sin((n+1/2)\theta)}{2\sin(\theta/2)}\]
\end{exercise}

\begin{exercise}{1.4.9.}
    Observe that the $n$th roots of $1$ are given by $\{1, \omega, \cdots, \omega^{n-1}\}$, where $\omega = e^{2\pi i/n}$. Assuming $n > 1$, show that $1+\omega+\cdots+\omega^{n-1} = 0$. Prove a similar result for the $n$th-roots of $-1$. 
\end{exercise}

\begin{exercise}{1.4.13.}
    Suppose that $p(z) = a_nz^n + \cdots + a_1z + a_0$ has real coefficients. 
    \begin{enumerate}
        \item Show that if $z_0$ is a root of $p$, then either $z_0$ is real or $\overline{z}_0$ is also a root of $p$. 
        \item Assuming the Fundamental Theorem of Algebra, show that $p$ must factor as a product: 
        \[ p(z) = a_n(z-r_1)\cdots(z-r_k)q_1(z)\cdots q_s(z)\]
        \item Factor $p(z) = z^4 + z^3 + z^2 + z + 1$ into a product of irreducible quadratics. 
    \end{enumerate}
\end{exercise}




\newpage

\subsection{Sequences and Series}
Recall that if $(a_n)_{n=1}^\infty$ is a sequence in $\C$ then the series 
\[ \sum_{n=1}^\infty a_n\]
converges if the sequence $(s_n)$ of partial sums converges and then:
\[\sum_{n=1}^\infty a_n = \lim_{n\to \infty} s_n \]
We say the series converges absolutely if $\sum_{n=1}^\infty |a_n| < \infty$. 

\begin{lemma}[W 1.2.9]
    An absolutely convergent series is convergent.
\end{lemma}
\begin{proof}
    Suppose $\sum_{n=1}^\infty |a_n| < \infty$ is absolutely convergent. Then given $\epsilon > 0$, $\exists N$ such that $n \geq N \implies \sum_{n=N}^\infty |a_n| < \epsilon$. Now if $m > n \geq N$, we have: 
    \[ |s_m - s_n| \leq \sum_{k=n+1}^m | a_k | \leq \sum_{k = N}^\infty |a_k| < \epsilon\]
    Thus, $(s_n)$ is Cauchy and by completeness of $\C$, it converges. 
\end{proof}

\begin{theorem}[W 1.1.30]
    Let $(a_n) \subset \C$. Then,
    \begin{enumerate}
        \item If $|a_n| < b_n$ and $\sum_{n=1}^\infty b_n < \infty$, then the series $\sum a_n$ is absolutely convergent. 
        \item If $\lim_{n \to \infty} \left|\frac{a_{n+1}}{a_n}\right| = L$, then $\sum_{n=1}^\infty a_n$ is absolutely convergent if $L < 1$ and diverges if $L > 1$. 
        \item Let $L = \limsup |a_n|^{1/n}$. If $L < 1$, then $\sum a_n$ converges absolutely and diverges if $L > 1$. 
    \end{enumerate}
\end{theorem}

Recall, the definition of a $\limsup$. For $(a_n)$, let $\alpha_n = \sup \{ a_k : k \geq n\}$. This is monotonic decreasing. Then, $\limsup_n a_n = \lim_n \sup_{k\geq n} a_k$. 

Recall, if $(f_n)$ is a sequence of $\C$ valued functions on $D \subseteq \C$ then we say $(f_n)$ converges pointwise on $D$ to some function $f: D \subset \C \to \C$ if:
\[ \lim_{n\to \infty} f_n(z) = f(z) \qquad \forall z \in D\]
We say $(f_n)$ converges uniformly to $f$ on $D$ if $\forall \epsilon > 0$, there exists $N$ such that $n \geq N$ implies
\[ |f_n(z)-f(z)| < \epsilon \qquad \forall z \in D\]

We use the same terminology for the series $\sum_{n=1}^\infty f_n$ by condering the appropriate partial sums. 

\begin{theorem}[W 1.31, Weierstrass M-test]
    Suppose $D \subseteq \C$ and $(f_n)$ is a sequence of $\C$-valued functions on $D$ such that $|f_n(z)| \leq M_n$ for all $z \in D$. If $\sum_{n=1}^\infty M_n < \infty$, then $\sum_{n=1}^\infty f_n$ converges uniformly on $D$ to some $f: D \subseteq \C \to \C$. 
\end{theorem}

\begin{proof}
    Note that $\forall z \in D$, $\sum_{n=1}^\infty f_n(z)$ converges to some $f(z) \in \C$ by comparision test. If $\epsilon > 0$, then $\exists N$ such that $n \geq N \implies \sum_{n=N}^\infty M_n < \epsilon$. If $n \geq N$, then
    \begin{align*}
        |f(z) - s_n(z)| &= |f(z) - \sum_{k=1}^n f_k(z)| \\
        &= \left|\sum_{k = n+1}^\infty f_k(z)\right| \\
        &\leq \sum_{k=n+1}^\infty |f_k(z)| \\
        &\leq \sum_{k=n+1}^\infty M_k < \epsilon
    \end{align*}
\end{proof}

\begin{definition}
    Let $(a_n)_{n=0}^\infty \subset \C$ and $z_0 \in \C$, then the series: 
    \[ \sum_{n=0}^\infty a_n(z-z_0)^n = a_0 + a_1(z-z_0) + \cdots \]
    is called a power series centered at $z_0$ with coefficients $a_k$. 
\end{definition}

\begin{theorem}[W 1.34]
    Consider  
    \[ P : \sum_{n=0}^\infty a_n(z-z_0)^n = a_0 + a_1(z-z_0) + \cdots \]
    Then, there exists $R \in [0, \infty]$ such that: 
    \begin{enumerate}
        \item $P$ converges absolutely if $|z-z_0| < R$
        \item $P$ diverges if $|z-z_0| > R$
        \item and if $0 < r < R$, then $P$ converges uniformly on $D_r(z_0)$. 
    \end{enumerate}
    Furthermore,
    \[ \frac{1}{R} = \limsup_n|a_n|^{1/n} \]
\end{theorem}

\begin{proof}
    Can assume $z_0 = 0$ without loss of generality. $P$ always converges at $z = 0$. If $P$ converges only at $z = 0$, then take $R = 0$ so that $(a)$ and $(b)$ hold and $(c)$ is vacuous. 
    
    Otherwise, suppose the $P$ converges at another point $z_1$ with $|z_1| > 0$. Then, $\exists M$ such that:
    \[ |a_nz_1^n| \leq M \qquad \forall n\]
    If $|z| < |z_1|$, then, 
    \begin{align*}
        |a_nz^n| = |a_nz_1^n| \left|\frac{z}{z_1}^n\right| \leq M \left|\frac{z}{z_1}^n\right|
    \end{align*}
    and $P$ converges absolutely at $z$ by the comparison test. 

    Let $R = \sup \{ |z| : P \text{ converges at } z\}$. If $|z| < R$, then $\exists z$ such that $P$ converges at $z$ and $|z| < |z_1|$. But then, $P$ converges absolutely at $z$. If $|z| > R$, we know that $P$ diverges at $z$. Thus, $(a)$ and $(b)$ hold with $R$. 

    If $0 < r < R$, then $P$ converges absolutely at $z = r$, and we can let $M_n = |a_n|r^n$ and then $P$ converges uniformly on $D_r(0)$ and (c) holds.
    Now let,
    \[ R_0^{-1} = \limsup_n |a_n|^{1/n}\]
    If $0 < |z| < R_0$, then
    \[ \limsup_n |a_nz^n|^{1/n} = R_0^{-1}|z| < 1\]
    Thus, $P$ converges absolutely at $z$. 
    
    If $|z| > R_0$, then, 
    \[  \limsup_n |a_nz^n|^{1/n} = R_0^{-1} |z| > 1\]
    Thus, $P$ diverges. 

    Thus, $R_0 = R$. 
\end{proof}

Recall, that a subset $D \subset \C$ is connected if it does not admit a non-trivial partition into relatively open subsets.
\begin{remark}
    $A \subset \C$ is connected if given open sets $U, V \in \C$ such that $\{ A \cap U, A \cap V \}$ is a partition and $A \cap U$ is not empty, then $A \cap V$ is empty. 
\end{remark} 

\begin{definition}
    We call a connected, open subset $D \subset \C$ a domain. 
\end{definition}

If $E \subset \C$ and $z \in E$, then 
\[ E(z) := \bigcup \{ A \subset \C : z \in A \subset E \text{ and } A \text{ connected} \}\]
Then $E(z)$ is connected and if $E(z) \cap E(w) \neq 0$ then, $E(z) = E(w)$. These form a partition of $A$ and are called the connected components of $E$. 

Since disks $D_r(z_0)$ are connected, it follows that the connected components of an open set $U$ are open. (W Ex. 2.1.2). That is, every open subset is a countable union of domains. 

We say $E \subset \C$ is path connected if given $z, w \in E$, there is a continous function: 
\[ \gamma: [0, 1] \to E \]
such that $\gamma(0) = z$ and $\gamma(1) = w$. Since $[0, 1]$ is connected, it follows that path-connected sets are connected. 

For an connected open set, the converse holds (because disks are path-connected). 

Questions for next time. 
$(a_n) \subset \R$. Suppose $\sum_{n=1}^\infty a_n$ converges. 
\begin{enumerate}
    \item[Q1.] Does $\sum_{n=1}^\infty a_n^2$ converge? 
    \item[Q2.] Does $\sum_{n=1}^\infty a_n^3$ converge? 
\end{enumerate}

















\end{document}