\documentclass[12pt]{article}


\include{../style}


\begin{document}


\input{title}


\section{Intro to Toric Geometry:}

There are $2$ mottos in toric geometry. 
\begin{enumerate}
    \item Toric geometry is the study of solutions to polynomoial equations in the preserve of a large torus.
    \item The action of a torus should give combinatorial/algebraic structure.
\end{enumerate}

To make sense of this, we need to understand what solutions to polynomial equations are and what is a large torus. 

A geometric torus is $\underbrace{S^1 \times S^1 \times \cdots \times S^1}_{n \text{ times}}$. An algebraic torus is $(\C^\times)^\times$ or, more generally, $(k^\times)^n$ for some field $k$. 

We will now do an interlude in basic algebraic geometry. 

Let $k$ be a field. We call $\A_k^n = k^n$ the affine $n$-space. Next, we define algebraic sets and the Zariski topology. 

We give some examples of algebraic sets: The vanishings of $x^2+y^2$, $xy$, $x^2y-y$, and $z^2-x^2-y^2$ in the appropriate affine spaces. 

\begin{definition}
    An affine algebraic vareirt is an algebraic subset of $\A^n_k$ such that it is irreducible in the Zariski topology.
\end{definition}

\begin{theorem}[Nullstellensatz]
    There is an order reversing bijection:
    \[ \left\{\text{Algebraic varieties in $\A^n_k$} \right\} \leftrightarrow \left\{ I \subseteq k[x_1, \cdots, x_n] \text{ such that $I$ is prime. }\right\}\]
\end{theorem}

Coming back to toruses, note that $k^\times \subset \A^1$ is a torus living in our affine space. Thus, $A^1$ is a toric variety. Similarly, $(k^\times)^n = \A^n \setminus \V(x_1\cdots x_n) \subseteq \A^n$ is an big torus. Hence, $\A^n$ is a toric variety. 

\begin{definition}
    If $X \subseteq \A^n$ is an algebraic set, the coordinate ring is: 
    \[ k[X] = k[x_1,\cdots, x_n]/I_X\]
    where $I_X = \langle f \in k[x_1, \cdots, x_n] | f(p) = 0 \, \forall x \in X \rangle$.
\end{definition}

\begin{lemma}
    If $f \in S = k[x_1, \cdots, x_n]$, then the set $D(f) = \A^n \setminus \V(f)$ is such that $k[D(f)] \equiv S\left[\frac{1}{f}\right]$
\end{lemma}

Then, as examples, we get that the large tori:
\begin{enumerate}
    \item $k[(k^\times)] = k[x, x^{-1}]$
    \item $k[(k^\times)^n] = k[x_1, x_1^{-1}, \cdots, x_n, x_n^{-1}]$
\end{enumerate}

Now we can define what a toric variety is. 
\begin{definition}
    An affine toric vareity is an affine algebraic variety $X$ together with an open dense torus $T \subseteq X$ such that the action of $T$ on itself extends to $X$. That is, there is an action $k^\times \times \A^1 \to \A$ that restricts to the torus' action on itself on $k^\times \times k^\times$. 
\end{definition}

We now discuss what the action of the torus means. Let $T = (k^\times)$. Then $T$ is also a group with multiplication $(s,t) \mapsto st$ and inverse $t \mapsto t^{-1}$.

\begin{example}
    Let $k^\times \subset \A^1$. Then, $k^\times$ acts on itself. We extend this by letting the action on $0$ be such that $t \times 0 = 0$ for all $t \in k^\times$. 
\end{example}

Now we make all of this precise. We have the following definition:
\begin{definition}
    An algebraic group is an algebraic variety $G$ together with maps: 
    \[ \times: G \times G \to G \qquad (-)^{-1}: G \to G\]
    that are regular and satisfy the usual group axioms.
\end{definition}

\begin{example}
    $G = (k^\times)^n$ with coordinate with multiplication and inverses. 
\end{example}

\begin{definition}
    A split torus over a field $k$ is algebraic group $G$ isomorphisc over $k$ to $(k^\times)^n$ for some $n$. 
\end{definition}

\begin{definition}
    An algebraic torus over a field $k$ is an algebraic group $T$ such that after an extension, $T \times_k F \cong (F^\times)^n$. 
\end{definition}

\begin{remark}
    To motivate this definition, consider $S^1$. We want $S^1$ to be a torus. That is, $S^1 = \V(x^2+y^2-1) \subseteq \A^2_\R$ is not $(\R^\times)^n$ for any $n$. However, if we consider $S^1 = \V(x^2+y^2-1) \subseteq \A^2_\C$, we can factor the polynomial to write it as $\V(zw-1)$. Considering $\C[z,w]/\langle zw-1\rangle \cong \C[x, x^{-1}]$. 
\end{remark}

\begin{definition}
    An affine toric variety is an affine algebraic variety $X$ together with a torus $T \subseteq X$ that is open and dense together with an algebraic action: 
    \[ \xymatrix{T \times X \ar[r] & T \\ T \times T \ar[u] \ar[r] & T \ar[u] } \]
\end{definition}

\begin{definition}
    Let $X \subseteq \A^n$ and $Y \subseteq \A^m$ be affine algebraic varieties. A morphism is globally given by polynomials $(f_1, \cdots, f_m)$ that restrict to a map from $X$ to $Y$.
\end{definition}

\begin{lemma}
    $\Phi: X \to Y$ is a morphism of algebraic varities if and only if there is an induced (pullback) map of rings: 
    \[ \Phi^*: k[Y] \to k[X]\]
\end{lemma}

\begin{example}[Toric Varieties]
    .
    \begin{enumerate}
        \item $X = (k^\times)^n$
        \item $X = \A^1$
        \item $X = \A^n$. Extend entry-wise. 
        \item $X = \V(x^3-y^2)$
    \end{enumerate}
\end{example}

\end{document}